\documentclass[12pt, a4paper]{scrartcl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=0.5in]{geometry}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}

\usepackage{xinttools}
\usepackage[nomessages]{fp}
\usepackage{tabularx}
\usepackage{tcolorbox}

\setlength{\parindent}{0pt}

\usepackage[pdftex]{insdljs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parameter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Values can be changed, but rarely improve the result
\def\boardWidth{11}
\def\boardHeight{\boardWidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Javascript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{insDLJS}[]{JSDateiname}{crossword}

const GAME_DESC = "This is a crossword puzzle. Your goal is to fill all cells with the correct\
character. Usually the connected character build a word. When hovering over the arrows a hint\
is shown, indicating which word should be entered into a row or column.";

% Outside variables
const BOARD_WIDTH = AFMakeNumber(\boardWidth);
const BOARD_HEIGHT = AFMakeNumber(\boardHeight);
const SCREEN_TEXT_SIZE = 300;
% Maximum amount of words in the puzzle
% OBACHT: This count is not very accurate, since the random length of the words highly
% influence how many words can be placed onto the board.
var wordCount = 10;

% Constants
const EMPTY = -1;

% For indexing
const M = 0;
const N = 1;
const ORI_IDX = 2;

% The game allows for upto 4 directions (up, down, left, right)
% Diagonals also work, but are not supported by the arrows and the hint system
var ORIENTATIONS = [
    [1, 0], [0, 1]%,
    %[-1, 0], [0, -1]
]

% Globals
% The game- and the solution array
var complBoard = new Array();
var solution = new Array();

% Color data
const HIGHLIGHT_TRUE_COLOR = [ "RGB", 0.100, 0.800, 0.176 ];
const HIGHLIGHT_FALSE_COLOR = [ "RGB", 0.984, 0.100, 0.176 ];

% Word data
const WORD_LIST = [
    ["WIND", "BEAN", "HOOK", "COAT", "EASY", "JOKE"], % 4
    ["LEARN", "FAITH", "PROOF", "SOLID", "ALOOF", "PEACE", "BELLY", "ALLOW"], % 5
    ["MARKET", "PERSON", "PRAISE", "FINISH"], % 6
    ["FRECKLE", "COMBINE", "ARCHIVE", "INSPIRE"], % 7
    ["NONSENSE", "HARDWARE"], % 8
    ["EVOLUTION", "ORCHESTRA", "OPERATION", "POLICEMAN"], % 9
    ["COMPROMISE"], % 10
    ["COMPETITION", "ANNIVERSARY"] % 11
]

% Containing hints for the word that is to be found
% https://www.the-crossword-solver.com/search
const HINT_LIST = [
    ["air moving", "edible pod", "fish trap", "blazer", "like childs play", "pun"], % 4
    ["get to know", "strong belief", "evidence", "not hollow", "hardly warm",
        "state of calm", "abdomen", "give permission"], % 5
    ["place of trade", "an individual", "expressed approval", "goal"], % 6
    ["melanin spot", "add together", "databank", "stimulate activity"], % 7
    ["without meaning", "computer equipment"], % 8
    ["gradual development", "large band", "surgery", "law enforcer"], % 9
    ["trade-off"], % 10
    ["duel to gain", "recurring yearly"] % 11
]

% A modifyable copy of the WORD_LIST
var wordList = [];

% Allows to save the currently available positions
% of each char between 'A' and 'Z'
var charPositions = [
    [], [], [], [], [], [], [], [], [], [],
    [], [], [], [], [], [], [], [], [], [],
    [], [], [], [], [], []
];

% A list of coordinates for each word
var curWords = [];

% Arrow symbols
const SYMBOLS = [
    String.fromCharCode(0x2193),
    String.fromCharCode(0x2192),
    String.fromCharCode(0x2191),
    String.fromCharCode(0x2190)
];

%%%%%%%%%%
% Helper %
%%%%%%%%%%
/**
 * Returns a random number between 0 and the param.
 * @param {Number} max The upperbound
 */
function getRandomInt(max) {
    return Math.floor(Math.random() * max);
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Initialisation and Restart %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialise the default game state.
 */
function initialise() {
    % Init the GUI
    initialiseButtons();

    % Create an empty board
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        var row = new Array();
        var solRow = new Array();
        for (var n = 0; n < BOARD_WIDTH; n++) {
            row.push(EMPTY);
            solRow.push(EMPTY);
        }
        complBoard.push(row);
        solution.push(solRow);
    }

    % Copy word list
    for (var i = 0; i < WORD_LIST.length; i++) {
        var tmp = [];
        for (var j = 0; j < WORD_LIST[i].length; j++) {
            tmp.push(WORD_LIST[i][j]);
        }
        wordList.push(tmp);
    }

    createBoard();
    % Hide unused cells
    drawAndHideAll();
}

/**
 * Initialise all buttons from the GUI.
 * For example add callbacks and set the correct colors.
 */
function initialiseButtons() {
    % Disables the rectangle around a button after the click
    app.focusRect = false;

    this.getField("cmDirs").currentValueIndices = 0;
    this.getField("cmWords").currentValueIndices = 5;
    wordCount = this.getField("cmWords").value;

    % Assign each button the coresponding function
    this.getField("restart").setAction("MouseUp", "restart();");
    this.getField("checkall").setAction("MouseUp", "checkAll();");

    % Each cell needs to be connected to an input and a hover function
    var cell;
    var funcName = "cellClicked";
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            var callbackName = funcName + "(" + m.toString() + "," + n.toString() + ");";
            cell = this.getField("cell" + m + "-" + n);
            cell.setAction("OnBlur", callbackName);
            cell.textSize = SCREEN_TEXT_SIZE / Math.max(BOARD_HEIGHT, BOARD_WIDTH);
            cell.charLimit = 1;

            % Add hover callbacks to cells
            var showCallback = "showHint" + "(" + m.toString() + "," + n.toString() + ");";
            cell.setAction("MouseEnter", showCallback);

            var hideCallback = "hideHint" + "(" + m.toString() + "," + n.toString() + ");";
            cell.setAction("MouseExit", hideCallback);
        }
    }

    % The overlay used for the hint
    var overlay = this.getField("overlay");
    overlay.textSize = SCREEN_TEXT_SIZE / Math.max(BOARD_HEIGHT, BOARD_WIDTH);
    overlay.textColor = color.white;
    overlay.fillColor = color.black;

    % Tooltip setup
    this.getField("tooltipbtn").setAction("MouseDown", "tooltip(true);");
    this.getField("tooltipbtn").setAction("MouseUp", "tooltip(false);");

    printInfoText("Solve this puzzle.");
}

/**
 * Clear everything and restart the game.
 */
function restart() {
    % Update word count
    wordCount = this.getField("cmWords").value;
    % Use GUI to set amount of orientations
    if (this.getField("cmDirs").value == 2) {
        ORIENTATIONS = [
            [1, 0], [0, 1]
        ];
    } else {
        ORIENTATIONS = [
            [1, 0], [0, 1],
            [-1, 0], [0, -1]
        ];
    }

    % Reset both boards
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            solution[m][n] = EMPTY;
            complBoard[m][n] = EMPTY;
        }
    }

    % Copy the word list
    wordList = [];
    for (var i = 0; i < WORD_LIST.length; i++) {
        var tmp = [];
        for (var j = 0; j < WORD_LIST[i].length; j++) {
            tmp.push(WORD_LIST[i][j]);
        }
        wordList.push(tmp);
    }

    % Reset all char positions since there are no entries in the beginning
    for (var char = 0; char < charPositions.length; char++) {
        charPositions[char] = [];
    }

    % Reset the words to be found
    curWords = [];
    % Create the board, by creating a solution and a list of current words
    createBoard();

    % Disable highlight and refresh rendering
    highlightAll(color.gray);
    drawAndHideAll();

    printInfoText("Restarted game.");
}

/**
 * Enable or disable the tooltip.
 *
 * @param {Boolean} on Enable or disable tooltip.
 */
function tooltip(on) {
    if (on) {
        % Move the tooltip field to the center of the screen
        % and adjust the size so the text can be displayed
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = false;
        field.value = GAME_DESC;

        field.multiline = true;
        field.textSize = 16;
        % height 842, width 596
        % upper-left x, upper-left y, lower-right x and lower-right y
        field.rect = [128, 601, 468, 401];

        this.getField("tooltiptxt").setFocus();

        field.delay = false;
    } else {
        % Remove the field such that it is not visible
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = true;
        field.delay = false;
    }
}

%%%%%%%%%%%%%%%%%%
% Board creation %
% https://stackoverflow.com/questions/943113/algorithm-to-generate-a-crossword
%%%%%%%%%%%%%%%%%%
/**
 * Creates a board, by adding words from the word list to the solution array when possible.
 * This is determined by checking all already placed characters for intersections
 * with each available word.
 * The words character positions are also saved inside another array.
 */
function createBoard() {
    % Create list of random length
    var lengthList = [];
    for (var i = 0; i < wordCount; i++) {
        var len = getRandomInt(Math.min(BOARD_WIDTH, BOARD_HEIGHT) - 1);
        lengthList.push(len);
    }
    % Sort length list
    lengthList.sort(function(a, b) {
        return b - a;
    });

    % Create and add the specified amount of words
    % OBACHT: The algorithm tries to fit each word once,
    % if there was not valid position the word is removed and not used again.
    % This could be changed by moving the splice-method from getWordWithLen()
    % into this loop after adding a word, but in that case the word would be
    % marked anotherway to prevent testing a word multiple times.
    for (var i = 0; i < wordCount; i++) {
        % Get a word with the current length
        var word = getWordWithLen(lengthList[i]);

        % TODO
        % If is is the first word, place its center letter
        % in the middle of the board
        if (i == 0) {
            var center = Math.floor(word.length / 2.0);
            var oriIdx = getRandomInt(ORIENTATIONS.length);
            var m = Math.floor(BOARD_HEIGHT * 0.5);
            var n = Math.floor(BOARD_WIDTH * 0.5);
            var charPos = word.charAt(center).charCodeAt() - 65;
            charPositions[charPos].push([m, n, oriIdx]);
        }

        % In case all words in the word list where tested
        if (word == "###") {
            return;
        }
        % Place at valid position
        % If this is not possible try to add another word
        if (!addWord(word)) {
            i--;
        }
    }
}

/**
 * Gets a random word from the word list with the given length.
 * If the length is smaller or bigger than allowed the closest length is used.
 * If there are no words left with this length other length are chosen,
 * until the word list is completely empty.
 * @param {Number} len The length of the word.
 * @return {String} The found word.
 */
function getWordWithLen(len) {
    % Check for out of bounds
    var minLen = WORD_LIST[0][0].length;
    var maxLen = WORD_LIST[WORD_LIST.length - 1][0].length;
    if (len < minLen) {
        len = minLen;
    } else if (len > maxLen) {
        len = maxLen;
    }

    % Check the list at the current length. If there are no words
    % left try another length until a word is found or all sizes are checked
    var lIdx = len - 4;
    for (var tmp = 0; wordList[lIdx].length == 0; tmp++) {
        if (tmp >= WORD_LIST.length) {
            % The list is empty
            return "###";
        }
        lIdx = (lIdx + 1) \% WORD_LIST.length;
    }

    % Return a random word for the given length from the list
    var wIdx = getRandomInt(wordList[lIdx].length);
    var word = wordList[lIdx][wIdx];
    % Remove the word such that it can not be tested again
    wordList[lIdx].splice(wIdx, 1);

    return word;
}

/**
 * Adds a word to the solution and the current list of words,
 * if a valid position is found.
 * @param {String} word The word to add.
 */
function addWord(word) {
    % If there is no valid position indicate the failure
    var posInfo = getValidPosition(word);
    if (posInfo.length == 0) {
        return false;
    }
    var oriIdx = posInfo[ORI_IDX];
    var ori = ORIENTATIONS[oriIdx];
    % Get one cell before the word to add start icon
    var m = posInfo[M] - ori[M];
    var n = posInfo[N] - ori[N];

    var wordCoords = [];
    wordCoords.push([m, n]);
    % Place the start icon and the index of the word
    complBoard[m][n] = SYMBOLS[posInfo[ORI_IDX]];
    solution[m][n] = curWords.length;

    % Iterate all chars and add them to the solution
    for (var l = 0; l < word.length; l++) {
        m += ori[M];
        n += ori[N];

        var char = word.charAt(l);
        solution[m][n] = char;
        % for each char save the position in the char array
        charPositions[(char.charCodeAt() - 65)].push([m, n, oriIdx]);
        % Push character coordinates
        wordCoords.push([m, n]);
    }
    % Add the coordinates to the current words array
    curWords.push(wordCoords);
    return true;
}

/**
 * Tests if the given word has any valid positions at which to be placed.
 * For this each character of the word is iterated checking if this character
 * can be found on the board.
 * Select a position if placing the word there would not be out of bounds and
 * would not collide with other words. All options are tested, while the one
 * having the most occurrences is chossen.
 * Example: if there would be 3x "e", 2x "f" - "e" would be chosen, unless
 * none of these are valid due to collisions.
 *
 * @param {String} word The word to get a valid position for.
 */
function getValidPosition(word) {
    var m = 0;
    var n = 0;
    var oriIdx = 0;

    % Used for saving the best combination of len, char and position
    var len = 0;
    var lastChar = 0;
    var lastPos = 0;

    var result = [];

    % Iterate all characters of the word
    for (var l = 0; l < word.length; l++) {
        var char = word.charAt(l).charCodeAt() - 65;
        % If there are idientical characters available
        if (charPositions[char].length > len) {

            % Iterate all possible positions of this character
            for (var pos = 0; pos < charPositions[char].length; pos++) {
                var posInfo = charPositions[char][pos];

                % Alternate orientation - otherwise the orientation
                % from words attached to another word always be the same
                % OBACHT: only one direction is tested, it might be possible,
                % that the other direction would have worked
                var add = 1 + getRandomInt(2) * 2;
                oriIdx = (posInfo[ORI_IDX] + add) \% ORIENTATIONS.length;
                var ori = ORIENTATIONS[oriIdx];

                % Calculate start position
                m = posInfo[M] - l * ori[M];
                n = posInfo[N] - l * ori[N];
                % Check if the word would be override something or be OOB
                if (checkCollisionAndOOB(word, [m, n, oriIdx])) {
                    % Save the startposition
                    result = [m, n, oriIdx];
                    len = charPositions[char].length;
                    lastChar = char;
                    lastPos = pos;
                }
            }
        }
    }
    % Remove char if there was a match otherwise return an empty array
    if (result.length != 0) {
        charPositions[lastChar].splice(pos, 1);
    }
    return result;
}

/**
 * Checks for collisions and out of bounds.
 * Collision would be if a cell is already occupied by a character
 * different from the one that shall be placed.
 * Furthermore a word can collide if a neighbouring cell is occupied,
 * since this would alter the neighbouring word.
 *
 * @param {String} word The word to test for collsion.
 * @param {Array} posInfo The start position and the orientation.
 * @return {Boolean} True if there is no collision, else false.
 */
function checkCollisionAndOOB(word, posInfo) {
    var m = posInfo[M];
    var n = posInfo[N];
    var oriIdx = posInfo[ORI_IDX];
    var ori = ORIENTATIONS[oriIdx];

    % Test the cell infront of the word (for the orientation symbol)
    var tmpM = m - ori[M];
    var tmpN = n - ori[N];
    if (tmpN >= 0 && tmpN < BOARD_WIDTH && tmpM >= 0 & tmpM < BOARD_HEIGHT) {
        if (solution[tmpM][tmpN] != EMPTY) {
            return false;
        }
    } else {
        % OOB
        return false;
    }

    for (var l = 0; l < word.length; l++) {
        % OOB
        if (n < 0 || n >= BOARD_WIDTH || m < 0 || m >= BOARD_HEIGHT) {
            return false;
        }
        % Collision
        if (solution[m][n] == EMPTY) {
            % Specify the direction of the neighbourhood (orthogonal)
            var neighOriIdx = (oriIdx + 1) \% ORIENTATIONS.length;
            if (!checkNeighbourhood(m, n, neighOriIdx)) {
                return false;
            }
        } else if (solution[m][n] != word.charAt(l)) {
            return false;
        }

        m += ori[M];
        n += ori[N];
    }

    % Test the cell behind the word (no OOB test)
    if (n >= 0 && n < BOARD_WIDTH && m >= 0 & m < BOARD_HEIGHT) {
        if (solution[m][n] != EMPTY) {
            return false;
        }
    }

    return true;
}

/**
 * Checks the two neighbouring cells in the +- direction of the given
 * orientation for beeing empty.
 *
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 * @param {Number} oriIdx The orientation index.
 * @return {Boolean} True if neighbouring cells are empty, else false.
 */
function checkNeighbourhood(m, n, oriIdx) {
    var neighOri = ORIENTATIONS[oriIdx];
    var neigh1M = m + neighOri[M];
    var neigh1N = n + neighOri[N];
    var neigh2M = m - neighOri[M];
    var neigh2N = n - neighOri[N];

    % Ignore OOB
    if (neigh1N >= 0 && neigh1N < BOARD_WIDTH && neigh1M >= 0 && neigh1M < BOARD_HEIGHT) {
        % If non empty return false
        if (solution[neigh1M][neigh1N] != EMPTY) {
            return false;
        }
    }
    if (neigh2N >= 0 && neigh2N < BOARD_WIDTH && neigh2M >= 0 && neigh2M < BOARD_HEIGHT) {
        if (solution[neigh2M][neigh2N] != EMPTY) {
            return false;
        }
    }
    return true;
}

%%%%%%%%%%%%%
% Gamelogic %
%%%%%%%%%%%%%
/**
 * Assignes the current cell value to the complBoard array.
 * Used for updating the array after an input (OnBlur event).
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 */
function cellClicked(m, n) {
    var cell = this.getField("cell" + m + "-" + n);
    % Revert changes to the arrow cells
    if (complBoard[m][n] > "Z") {
        cell.value = complBoard[m][n];
    } else {
        % Convert to uppercase
        if ("a" <= cell.value && cell.value <= "z") {
            cell.value = cell.value.toUpperCase();
            complBoard[m][n] = cell.value;
        } else if ("A" <= cell.value && cell.value <= "Z") {
            complBoard[m][n] = cell.value;
        } else {
            % If the input was not a letter remove the symbol
            cell.value = "";
            complBoard[m][n] = EMPTY;
        }
    }
}

/**
 * Check the complete board for correct or incorrect inputs
 * and mark these correspondingly. Only complete words are marked.
 * Indicate when the game is over.
 */
function checkAll() {
    var m = 0;
    var n = 0;

    var gameover = true;
    % Iterate list of words
    for (var w = 0; w < curWords.length; w++) {
        var wordComplete = true;
        % Check if current word is correct
        for (var c = 1; c < curWords[w].length; c++) {
            m = curWords[w][c][M];
            n = curWords[w][c][N];

            if (solution[m][n] != complBoard[m][n]) {
                wordComplete = false;
                gameover = false;
            }
        }

        % Mark current word as current or incorrect
        for (var c = 1; c < curWords[w].length; c++) {
            m = curWords[w][c][M];
            n = curWords[w][c][N];

            if (wordComplete) {
                printInfoText("Found correct word!");
                highlight(m, n, HIGHLIGHT_TRUE_COLOR);
            } else {
                highlight(m, n, HIGHLIGHT_FALSE_COLOR);
            }
            draw(m, n);
        }
    }

    if (gameover) {
        printInfoText("Gameover!");
    }
}

/**
 * Checks if a cell is an starting cell for a word (arrow cell).
 * If so activate the overlay.
 * For this the word index is used to get the rect of the first and
 * last cell and adjust the dimensions of the overlayfield.
 * The hint text is rotated if necessary.
 *
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 */
function showHint(m, n) {
    if (complBoard[m][n] > "Z") {
        const START = 1;
        var wIdx = solution[m][n];

        % Get the coordinates of this words cells
        var startM = curWords[wIdx][START][M];
        var startN = curWords[wIdx][START][N];
        var endM = curWords[wIdx][curWords[wIdx].length - 1][M];
        var endN = curWords[wIdx][curWords[wIdx].length - 1][N];

        var startCell = this.getField("cell" + startM + "-" + startN);
        var endCell = this.getField("cell" + endM + "-" + endN);

        % Get the new rect positions
        % upper-left x, upper-left y, lower-right x and lower-right y
        var uLx = Math.min(startCell.rect[0], endCell.rect[0]);
        var uLy = Math.max(startCell.rect[1], endCell.rect[1]);
        var lRx = Math.max(startCell.rect[2], endCell.rect[2]);
        var lRy = Math.min(startCell.rect[3], endCell.rect[3]);

        var newRect = [uLx, uLy, lRx, lRy];
        % Adjust overlayfield
        var overlay = this.getField("overlay");
        overlay.hidden = false;
        overlay.rect = newRect;
        overlay.value = getHintText(wIdx);
        % Rotate depending on the dimensions (length vs width)
        if (lRx - uLx < uLy - lRy) {
            overlay.rotation = 90;
        } else {
            overlay.rotation = 0;
        }
    }
}

/**
 * Checks if a cell is an starting cell for a word (arrow cell).
 * If so deactivate the overlay.
 * Is used on MouseExit.
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 */
function hideHint(m, n) {
    % Ensure arrow cell
    if (complBoard[m][n] > "Z") {
        % Just hide the overlayfield, no need to adjust it
        var overlay = this.getField("overlay");
        overlay.hidden = true;
    }
}

/**
 * Searches the WORD_LIST for the initial index of the given word
 * and uses this index to access the HINT_LIST.
 * @param {Number} wIdx The words index to reconstruct the word.
 * @param {String} The hint belonging to the given word.
 */
function getHintText(wIdx) {
    % Reconstruct the word
    var word = "";
    for (var c = 1; c < curWords[wIdx].length; c++) {
        var char = solution[curWords[wIdx][c][M]][curWords[wIdx][c][N]];
        word += char;
    }

    % Iterate all length rows of the word list
    for (var l = 0; l < WORD_LIST.length; l++) {
        for (var w = 0; w < WORD_LIST[l].length; w++) {
            % https://stackoverflow.com/questions/1179366/is-there-a-javascript-strcmp
            if (word == WORD_LIST[l][w]) {
                return HINT_LIST[l][w];
            }
        }
    }
}

%%%%%%%%%%%%%%%%%%%%%
% Draw and coloring %
%%%%%%%%%%%%%%%%%%%%%
/**
 * Draw all cells.
 */
function drawAndHideAll() {
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            % Redraw only if not hidden
            if (!hide(m, n)) {
                draw(m, n);
            }
        }
    }
}

/**
 * Since only one cell is updated with each input,
 * only this cell needs to be redrawn.
 *
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 */
function draw(m, n) {
    var cell = this.getField("cell" + m + "-" + n);
    cell.delay = true;
    % Bigger than "z" are the arrows
    if (complBoard[m][n] > "Z") {
        cell.value = complBoard[m][n];
        cell.textColor = color.white;
        cell.fillColor = color.black;
    } else if (complBoard[m][n] != EMPTY) {
        cell.value = complBoard[m][n];
        cell.textColor = color.black;
        cell.fillColor = color.white;
    } else {
        cell.value = "";
        cell.textColor = color.black;
        cell.fillColor = color.white;
    }
    cell.delay = false;
}

/**
 * Toggles the hidden state of the given cell,
 * depending on the value in the solution array.
 * If the solution is empty the cell is hidden.
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 */
function hide(m, n) {
    var c = this.getField("cell" + m + "-" + n);
    % If the solution is empty the cell must be hidden
    if (solution[m][n] != EMPTY) {
        c.hidden = false;
        return false;
    } else {
        c.hidden = true;
        return true;
    }
}

/**
 * Highlights all cells with the given color.
 * @param {Array} color The color array.
 */
function highlightAll(color) {
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            highlight(m, n, color);
        }
    }
}

/**
 * Highlights the given cell with the given color.
 *
 * @param {Number} m The row index.
 * @param {Number} n The column index.
 * @param {Array} color The color array.
 */
function highlight(m, n, color) {
    var field = this.getField("cell" + m + "-" + n);
    field.delay = true;
    field.borderColor = color;
    field.delay = false;
}

/**
 * Print information about the winner and the gamestate.
 */
function printInfoText(text) {
    var field = this.getField("info");
    field.delay = true;
    field.value = text;
    field.delay = false;
}

\end{insDLJS}

\OpenAction{/S /JavaScript /JS (initialise();)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dokument
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

    \begin{Form}

        % Header
        \begin{multicols}{2}
            % Title
            \section*{Crossword puzzle}
        \columnbreak
            % Tooltip object
            \begin{flushright}%
                \PushButton[name=tooltipbtn, bordercolor=, backgroundcolor=, borderwidth=0]{%
                    \begin{tcolorbox}[width=20pt, height=20pt, left=3pt, top=0pt]
                        \centering?\strut{}
                    \end{tcolorbox}%
                }
            \end{flushright}%
        \end{multicols}

        % Dynamically adjust the cell width and height to the number of cells
        % Calculate the max width and height of a cell
        \FPeval{\resultW}{\boardWidth * 3 - 2} % chktex 8
        \def\cellWidth{\dimexpr (\linewidth-\resultW pt)/\boardWidth \relax}

        \FPeval{\resultH}{\boardHeight * 3 + 3}
        \def\cellHeight{\dimexpr (500 pt -\resultH pt)/\boardHeight \relax}

        % The game board
        \begin{tcolorbox}
            % Define the cell size via the smaller amount
            % Must be done here so the \linewidth has the correct value
            \ifdim\cellWidth<\cellHeight
                \def\cellsize{\cellWidth}
            \else
                \def\cellsize{\cellHeight}
            \fi

            \begin{center}
                \tiny
                \xintFor* #1 in {\xintSeq{0}{\boardHeight-1}} \do {%
                    \xintFor* #2 in {\xintSeq{0}{\boardWidth-1}} \do {%
                        \TextField[%
                            name=cell#1-#2, width=\cellsize, height=\cellsize,%
                            bordercolor=gray, align=1%
                        ]{}%
                        \xintifForLast{}{\hspace{3pt}}%
                    }\vspace{3pt}\\[-1pt]%
                }%
            \end{center}%
        \end{tcolorbox}

        %%%%%%%%%%%%%%%%%%%%%%%
        % Commandredifinition %
        % https://www.dickimaw-books.com/latex/admin/html/eforms.shtml
        %%%%%%%%%%%%%%%%%%%%%%%
        \def\DefaultHeightofText{14pt}
        \renewcommand*{\DefaultWidthofChoiceMenu}{2.5ex}
        \renewcommand*{\DefaultHeightofChoiceMenu}{\DefaultHeightofText}

        %%%%%%%%%%%%%%%%
        % GUI elements %
        %%%%%%%%%%%%%%%%
        \begin{center}
            % Game related buttons
            \begin{tabularx}{\textwidth}{@{} *{2}{X} @{}}%
                \begin{tcolorbox}
                    \TextField[name=info, width=\linewidth,
                        bordercolor=, backgroundcolor=, readonly]{\strut}
                \end{tcolorbox} &
                \begin{tcolorbox}
                    \centering
                    \ChoiceMenu[name=cmDirs, bordercolor=gray, width=1.5cm, combo]
                        {Directions: \strut}{2, 4}
                    \ChoiceMenu[name=cmWords, bordercolor=gray, width=1.5cm, combo]
                        {Words: \strut}{5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15}
                \end{tcolorbox}\\[-0.3cm]
                \PushButton[name=checkall, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Check input\strut
                    \end{tcolorbox}
                } &
                \PushButton[name=restart, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Restart game\strut
                    \end{tcolorbox}
                }
            \end{tabularx}
        \end{center}

        \TextField[name=tooltiptxt, bordercolor=, backgroundcolor=gray, readonly, hidden]{}

        \TextField[name=overlay, bordercolor=white, align=1, readonly, hidden]{}

    \end{Form}
\end{document}
