\documentclass[12pt, a4paper]{scrartcl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=0.5in]{geometry}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}

\usepackage{xinttools}
\usepackage[nomessages]{fp}
\usepackage{tabularx}
\usepackage{tcolorbox}

\setlength{\parindent}{0pt}

\usepackage[pdftex]{insdljs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parameter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Obacht: It is discouraged to use more than 50 particles the performance might be to bad
\def\particleCount{20}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% JavaScript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{insDLJS}[]{JSDateiname}{particles}

const GAME_DESC = "In this application you can see a small particle system.\
Via the GUI it is possible to choose one of the available.";

% Outside variables
const PARTICLE_COUNT = AFMakeNumber(\particleCount);
const ANIMATION_SPEED = 70;

% Constants
% Spawn dimensions
const PARTICLE_SIZE = 10;
const PARTICLE_SIZE_H = PARTICLE_SIZE / 2;
const PARTICLE_TEXT_SIZE = 10;

% Access variables
const X = 0;
const Y = 1;

% Identifier for the different particle systems
const SNOW_P = 0;
const EXPL_P = 1;
const FLOW_P = 2;

% Particle data keys
const STATE = 0;
const POS = 1;
const SYMB = 2;
const ROTATION = 3;
const MASS = 4;
const MOMENTUM = 5;
const WIDTH = 6;
const HEIGHT = 7;
const SIZE = 8;

% Initial state
const DEAD = -1;

% Globals
% Animation interval variable
var run;
% Particle information
var particleType = 0;
% Array of all particles and their data
var particles;
% Information-Object with the current particle system data
var particleSys = {
    aliveParticles: 0,
    finished: function() {
        return true;
    }
};

% Container to save the shift of a particle rect
var shift = [0, 0];

%%%%%%%%%%
% Helper %
%%%%%%%%%%
/**
 * Returns a random number between 0 and the parameter.
 * @param {Number} max The upper bound
 */
function getRandomInt(max) {
    return Math.floor(Math.random() * max);
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Initialization and Restart %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialize the default particle state.
 */
function initialize() {
    % Initialize the GUI
    initializeButtons();

    % Setup canvas, particles, etc
    setCanvasData();
    defaultParticleSys();
    selectParticlesystem(particleType);

    % Start the animation interval
    run = app.setInterval("runAll()", ANIMATION_SPEED);
}

/**
 * Initialize all buttons from the GUI.
 * For example add callbacks.
 */
function initializeButtons() {
    % Disables the rectangle around a button after the click
    app.focusRect = false;

    this.getField("particleType").currentValueIndices = 0;

    % Assign each button the corresponding function and disable the highlights
    this.getField("restart").setAction("MouseUp", "restart();");

    this.getField("particleType").currentValueIndices = 0;
    this.getField("particleType").commitOnSelChange = true;

    % Tooltip setup
    this.getField("tooltipbtn").setAction("MouseDown", "tooltip(true);");
    this.getField("tooltipbtn").setAction("MouseUp", "tooltip(false);");
}

/**
 * Restart the particle system and the interval.
 */
function restart() {
    app.clearInterval(run);

    % Setup particles, etc
    defaultParticleSys();
    selectParticlesystem(particleType);

    run = app.setInterval("runAll()", ANIMATION_SPEED);
}

/**
 * Enable or disable the tooltip.
 *
 * @param {Boolean} on Enable or disable tooltip.
 */
function tooltip(on) {
    if (on) {
        % Move the tooltip field to the center of the screen
        % and adjust the size so the text can be displayed
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = false;
        field.value = GAME_DESC;

        field.multiline = true;
        field.textSize = 16;
        % height 842, width 596
        % upper-left x, upper-left y, lower-right x and lower-right y
        field.rect = [128, 601, 468, 401];

        this.getField("tooltiptxt").setFocus();

        field.delay = false;
    } else {
        % Remove the field such that it is not visible
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = true;
        field.delay = false;
    }
}

%%%%%%%%%%%%%%%%
% Drawing loop %
%%%%%%%%%%%%%%%%
/**
 * Main loop used to emit new particles or move the current ones.
 */
function runAll() {
    % Check if selected particle system changed
    var guiValue = this.getField("particleType").currentValueIndices;
    if (particleType != guiValue) {
        particleType = guiValue;
        restart();
        return;
    }

    if (!particleSys.finished()) {
        processParticles();
    }
}

%%%%%%%%%%%%%%%%%%%
% Setup functions %
%%%%%%%%%%%%%%%%%%%
/**
 * Sets the canvas object to contain information about the sizes,
 * borders and the center of both canvas elements.
 */
function setCanvasData() {
    const CANVAS_RECT = [0, 842, 596, 0];
    const LEFT = CANVAS_RECT[0];
    const BOT = CANVAS_RECT[3];

    const halfHeight = (CANVAS_RECT[1] - BOT) * 0.5;
    const halfWidth = (CANVAS_RECT[2] - LEFT) * 0.5;

    canvas = {
        c: [LEFT + halfWidth, BOT + halfHeight],
        l: LEFT,
        r: CANVAS_RECT[2],
        t: CANVAS_RECT[1],
        b: BOT,
        halfHeight: halfHeight,
        halfWidth: halfWidth,
    };
}

/**
 * (Re)set the particle array and the particleSys object to its
 * default state. Also resets the physics attributes and the functions.
 */
function defaultParticleSys() {
    particles = Array.apply(null, Array(PARTICLE_COUNT)).map(_ => [
        DEAD, [0, 0], % STATE, POS
        0, 0, % SYMB, ROTATION
        2, [0, 0],  % MASS, MOMENTUM
        PARTICLE_SIZE, % WIDTH
        PARTICLE_SIZE, % HEIGHT
        PARTICLE_TEXT_SIZE % SIZE
    ]);

    particleSys = {
        iterationCount: Infinity,
        iterationCur: 0,
        aliveParticles: 0,
        alignment: "center",
        particleCount: PARTICLE_COUNT,
        particleSymbols: ["X"],
        particleLifetime: 0,
        particleMultiline: false,
        particleBold: false,
        probability: 100,
        gravity: [0, -9.81],
        force: [0, 5],
        energyReduction: 0.45,
        % FUNCTIONS
        emit: function(p) {
            particles[p][STATE]++;
            this.aliveParticles++;
            return true;
        },
        remove: function(p) {
            hideParticle(p);
            particles[p][STATE] = DEAD;
            this.aliveParticles--;
        },
        finished: function() {
            var finished = this.iterationCount < this.iterationCur;
            return finished && this.aliveParticles == 0;
        }
    };
}

/**
 * Set all particles once after system selection.
 */
function setUpParticles() {
    for (var p = 0; p < particles.length; p++) {
        var particle = this.getField("particle" + p);
        % particle.textFont = font.Cour;
        particle.alignment = particleSys.alignment;
        particle.richText = particleSys.particleMultiline || particleSys.particleBold;
        particle.textSize = particles[p][SIZE];
        particle.hidden = true;
    }
}

%%%%%%%%%%%%%%%%%%%%%%
% Particle Selection %
%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialize the particle system data depending on the type.
 * @param {Number} type The type of the chosen particle system.
 */
function selectParticlesystem(type) {
    if (type == SNOW_P) {
        snowParticles();
    } else if (type == EXPL_P) {
        explosionParticles();
    } else if (type == FLOW_P) {
        flowerParticles();
    }
}

/**
 * Creates a particle system for falling snow.
 * The snow is distributed along the top border of the document
 * and slowly falls down until it reaches the bottom border.
 */
function snowParticles() {
    const SNOW_SYMBOLS = [
        String.fromCharCode(0x2744),
        String.fromCharCode(0x2745),
        String.fromCharCode(0x2746),
        String.fromCharCode(0x2749)
    ];

    particleSys.particleSymbols = SNOW_SYMBOLS;
    particleSys.particleLifetime = SNOW_SYMBOLS.length;
    particleSys.probability = 99;

    setUpParticles();

    particleSys.emit = function(p) {
        if (getRandomInt(100) < particleSys.probability) {
            return false;
        }

        particles[p][SYMB] = getRandomInt(SNOW_SYMBOLS.length);
        particles[p][SIZE] = PARTICLE_SIZE;
        % Get random start position
        var posX = getRandomInt(canvas.r - PARTICLE_SIZE) + PARTICLE_SIZE_H;
        var posY = canvas.t - PARTICLE_SIZE_H;
        particles[p][POS] = [posX, posY];

        particles[p][STATE]++;
        this.aliveParticles++;
        return true;
    }

    % Circular move function
    particleSys.move = function(p) {
        % Use sin pattern to shift the position slightly
        shift[X] = Math.cos((particles[p][POS][X] + particles[p][POS][Y]) / 40.0) * 20;

        var moveSpeed = 4;
        particles[p][POS][Y] -= moveSpeed;
        % Ending lifecycle when out of render area
        if (particles[p][POS][Y] < canvas.b) {
            particles[p][STATE] = particleSys.particleLifetime + 1;
        } else {
            particles[p][STATE] = 0;
        }
    }
}

/**
 * Creates a particle system that resembles small explosions.
 * These are made out of three circle symbols that are iterated
 * and distributed over the whole document.
 */
function explosionParticles() {
    const CIRCLE_SYMBOLS = [
        String.fromCharCode(0x25CF),
        String.fromCharCode(0x25CB),
        % Obacht this character is slow and seems to be buggy (text size is altered)
        String.fromCharCode(0x25CC)
    ];

    const DIV = 3;
    particleSys.particleSymbols = CIRCLE_SYMBOLS;
    particleSys.particleLifetime = CIRCLE_SYMBOLS.length * DIV - 1;
    particleSys.probability = 50;

    setUpParticles();

    particleSys.emit = function(p) {
        if (getRandomInt(100) < particleSys.probability) {
            return false;
        }

        particles[p][SYMB] = 0;

        % Get random position
        var posX = getRandomInt(canvas.r - PARTICLE_SIZE) + PARTICLE_SIZE_H;
        var posY = getRandomInt(canvas.t - PARTICLE_SIZE) + PARTICLE_SIZE_H;
        particles[p][POS] = [posX, posY];

        particles[p][STATE]++;
        particles[p][SIZE] = PARTICLE_TEXT_SIZE;
        particles[p][WIDTH] = PARTICLE_SIZE;
        particles[p][HEIGHT] = PARTICLE_SIZE;
        this.aliveParticles++;
        return true;
    }

    % Circular move function
    particleSys.move = function(p) {
        % Increase size
        particles[p][SIZE] *= 1.1;
        particles[p][WIDTH] *= 1.1;
        particles[p][HEIGHT] *= 1.1;
        particles[p][SYMB] = Math.floor(particles[p][STATE] / DIV);
    }
}

/**
 * Creates a particle system with UTF8 flower symbols.
 * The symbols are shot into the air similar to a fountain.
 */
function flowerParticles() {
    const FLOWER_SYMBOLS = [
        String.fromCharCode(0x2740)
    ];

    particleSys.particleSymbols = FLOWER_SYMBOLS;
    particleSys.particleLifetime = 1000;
    particleSys.probability = 98;

    setUpParticles();

    particleSys.emit = function(p) {
        if (getRandomInt(100) < particleSys.probability) {
            return false;
        }

        % Create directional force
        particles[p][MASS] = 1;
        particles[p][MOMENTUM] = [(getRandomInt(100) - 50) / 5, 85];

        var scale = 10;
        particles[p][SIZE] = PARTICLE_TEXT_SIZE * scale;
        particles[p][WIDTH] = PARTICLE_SIZE * scale;
        particles[p][HEIGHT] = PARTICLE_SIZE * scale;

        particles[p][POS] = [canvas.halfWidth, 0];

        particles[p][STATE]++;
        this.aliveParticles++;
        return true;
    }

    % Creates a fountain of flowers
    particleSys.move = function(p) {
        % Apply physics and let them fall
        particles[p][POS] = applyGravityToParticle(p, canvas.b - particles[p][HEIGHT] - 10);

        % Ending lifecycle when out of render area
        if (particles[p][POS][Y] < canvas.b) {
            particles[p][STATE] = particleSys.particleLifetime + 1;
        } else {
            particles[p][STATE] = 0;
        }
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Drawing and Processing %
%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Process the currently active particle system,
 * by iterating all active particles.
 * If an active particle is also dead and emit is attempted.
 * Otherwise the particle is updated and moved.
 */
function processParticles() {
    for (var p = 0; p < Math.min(particles.length, particleSys.particleCount); p++) {
        % If the particle is dead ...
        if (particles[p][STATE] == DEAD) {
            % ... check whether new particles should be emitted
            var finished = particleSys.iterationCount < particleSys.iterationCur;
            if (!finished) {
                % ... do not process this particle if emitting it failed
                if (!particleSys.emit(p)) {
                    continue;
                }
            }
            % ... if not do not process this particle
            else {
                continue;
            }
        } else if (particleSys.particleLifetime < particles[p][STATE]) {
            particleSys.remove(p);
            continue;
        }

        particleSys.move(p);
        % Draw the particle rectangle
        moveParticleRect(p);
        % Process particle content and appearance
        showAndUpdateParticle(p);

        particles[p][STATE]++;
    }

    particleSys.iterationCur++;
}

/**
 * Adjust the visualization rectangle of the given particle,
 * by using position, width and height.
 * @param {Number} p The particle index.
 */
function moveParticleRect(p) {
    var particle = this.getField("particle" + p);

    var x = particles[p][POS][X] + shift[X];
    var y = particles[p][POS][Y] + shift[Y];
    var w = particles[p][WIDTH];
    var h = particles[p][HEIGHT];
    var rect = [x - w, y + h, x + w, y - h];

    particle.rect = rect;
}

/**
 * Adjust the value and appearance of the given particle.
 * For example: multiline, textfont, textsize, rotation.
 * @param {Number} p The particle index.
 */
function showAndUpdateParticle(p) {
    var particle = this.getField("particle" + p);
    particle.delay = true;

    if (particles[p][STATE] == 0) {
        particle.hidden = false;
    }
    if (particles[p][SIZE] != PARTICLE_TEXT_SIZE) {
        particle.textSize = particles[p][SIZE];
    }
    if (particles[p][ROTATION] != 0) {
        particle.rotation = particles[p][ROTATION];
    }

    var textIdx = particles[p][SYMB];
    % Determine if richText is needed
    if (particleSys.particleMultiline || particleSys.particleBold) {
        var spans = new Array();
        spans[0] = new Object();
        spans[0].text = particleSys.particleSymbols[textIdx];
        if (particleSys.particleBold) {
            spans[0].fontWeight = 700;
        }

        particle.richValue = spans;
    } else {
        particle.value = particleSys.particleSymbols[textIdx];
    }
    particle.delay = false;
}

/**
 * Hide the given particle.
 * @param {Number} p The particle index.
 */
function hideParticle(p) {
    var particle = this.getField("particle" + p);
    particle.hidden = true;
}

%%%%%%%%%%%
% Utility %
%%%%%%%%%%%
/**
 * Alters the position of the given particle by using gravity.
 * The floor can be used to achieve a jumping motion.
 * Very similar the implementation found here:
 * https://gamedev.stackexchange.com/questions/10277/equation-for-bouncing-graph
 * @param {Number} p The particle index.
 * @param {Number} floor The y position at which the floor should be.
 */
function applyGravityToParticle(p, floor) {
    const h = particles[p][HEIGHT];
    const g = particleSys.gravity;
    const f = particleSys.force;
    const m = particles[p][MASS];
    var pos = particles[p][POS];
    var mom = particles[p][MOMENTUM];

    % Momentum += gravity + force
    mom = [mom[X] + g[X] + f[X], mom[Y] + g[Y] + f[Y]];
    % Velocity = momentum / mass
    var v = [mom[X] / m, mom[Y] / m];
    % Position += velocity
    pos = [pos[X] + v[X], pos[Y] + v[Y]];

    % If position is at floor & momentum heading downward
    if (pos[Y] < floor + h && mom[Y] < 0) {
        pos[Y] = floor + h;
        % Bouncing off direction
        var collisionNormal = [0, 1];
        var dot = mom[X] * collisionNormal[X] + mom[Y] * collisionNormal[Y];
        % Reflect
        mom = [mom[X] - collisionNormal[X] * 2 * dot, mom[Y] - collisionNormal[Y] * 2 * dot];
        % Energy loss from bounce.
        mom = [mom[X] * particleSys.energyReduction, mom[Y] * particleSys.energyReduction];
    }

    particles[p][MOMENTUM] = mom;
    return pos;
}

\end{insDLJS}

\OpenAction{/S /JavaScript /JS (initialize();)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

    \begin{Form}

        % Header
        \begin{multicols}{2}
            % Title
            \section*{Particles}
        \columnbreak
            % Tooltip object
            \begin{flushright}%
                \PushButton[name=tooltipbtn, bordercolor=, backgroundcolor=, borderwidth=0]{%
                    \begin{tcolorbox}[width=20pt, height=20pt, left=3pt, top=0pt]
                        \centering?\strut{}
                    \end{tcolorbox}%
                }
            \end{flushright}%
        \end{multicols}

        % Fill the page such that the remaining elements get pushed to the bottom
        \vspace*{\fill}

        % The particles for the particle system
        \xintFor* #1 in {\xintSeq{0}{\particleCount-1}} \do {%
            \TextField[name=particle#1, bordercolor=, backgroundcolor=, align=1, readonly, hidden]{}%
        }

        \TextField[name=tooltiptxt, bordercolor=, backgroundcolor=gray, readonly, hidden]{}

        %%%%%%%%%%%%%%%%%%%%%%%
        % Commandredifinition %
        % https://www.dickimaw-books.com/latex/admin/html/eforms.shtml
        %%%%%%%%%%%%%%%%%%%%%%%
        \renewcommand*{\DefaultWidthofChoiceMenu}{2.5ex}
        \renewcommand*{\DefaultHeightofChoiceMenu}{2.04ex}

        % Game related buttons
        \begin{center}%
            \begin{tabularx}{\textwidth}{@{} *{2}{X} @{}}%
                \PushButton[name=restart, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Restart particle system\strut
                    \end{tcolorbox}
                } &
                \begin{tcolorbox}
                    \ChoiceMenu[name=particleType, width=5cm,
                        bordercolor=gray, combo, edit=false
                    ]{Particlesystem:\strut}{Snow, Explosions, Flowers}
                \end{tcolorbox}
            \end{tabularx}
        \end{center}

    \end{Form}
\end{document}
