\documentclass[12pt, a4paper]{scrartcl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=0.5in]{geometry}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}

\usepackage{xinttools}
\usepackage{tabularx}
\usepackage{tcolorbox}

\setlength{\parindent}{0pt}

\usepackage[pdftex]{insdljs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parameter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% These variables should not be changed
\def\canvasCharWidth{80}
\def\canvasCharHeight{30}
\def\obstacleCount{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Javascript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{insDLJS}[]{JSDateiname}{sidescroller}

const GAME_DESC = "This game is a simple side-scroller,\
in which the player should evade objects that fly in his direction,\
while trying not to hit the bottom or top lines that limit the area.\
The player is only able to move up by pressing either w or space on his keyboard.\
If nothing is pressed the player will move downwards automatically.";

% Outside variables
const CANVAS_CHAR_W = AFMakeNumber(\canvasCharWidth);
const CANVAS_CHAR_H = AFMakeNumber(\canvasCharHeight);
const OBSTACLE_COUNT = AFMakeNumber(\obstacleCount);
const SCREEN_TEXT_SIZE = 800;
const TEXT_SIZE = 40;
const ANIMATION_SPEED = 5;

% Constants
const LINE_OFFSET = 2;
const START_TOP_LINE = LINE_OFFSET;
const START_BOT_LINE = CANVAS_CHAR_H - LINE_OFFSET - 1;

% Access constants
const X = 0;
const Y = 1;
const SYMB = 2;
const LEFT = 0;
const TOP = 1;
const RIGHT = 2;
const BOT = 3;
% Document dims: 842, 596
% Canvas dims
% upper-left x, upper-left y, lower-right x and lower-right y
const CANVAS_LTRB = [47.5, 770, 547.5, 241];
const CANVAS_HEIGHT = CANVAS_LTRB[TOP] - CANVAS_LTRB[BOT];
const CANVAS_WIDTH = CANVAS_LTRB[RIGHT] - CANVAS_LTRB[LEFT];
const CANVAS_CENTER_H = CANVAS_HEIGHT * 0.5 + CANVAS_LTRB[BOT];
const CANVAS_CENTER_W = CANVAS_WIDTH * 0.5 + CANVAS_LTRB[LEFT];
% Calculate units per char
const PER_CHAR = CANVAS_WIDTH / CANVAS_CHAR_W;
% Calculate units per line
const PER_LINE = CANVAS_HEIGHT / CANVAS_CHAR_H;
% Gravity stats
const GRAVITY = [0.0, -0.25];
var force = [0.0, 0.0];

const OBSTACLE_WIDTH = 20;
const PLAYER_WIDTH = 20;
const PLAYER_MASS = 0.5;

% Globals
% The gameloop interval
var gameInterval;
var gameover = false;
% The game duration
var charCounter = 0;
% Indicator which input element is focused currently
var focus = true;
% Player attributes
var playerMomentum = [0.0, 0.0];
var playerPos = [CANVAS_CENTER_W * 0.5 + PLAYER_WIDTH, CANVAS_CENTER_H];
% Obstacle array
var obstacles = [];

% Color data
% const COLORS = new Array(
%     [ "RGB", 0.843, 0.078, 0.058 ],
%     [ "RGB", 0.203, 0.603, 0.054 ],
%     [ "RGB", 0.078, 0.305, 0.560 ]
% );

% Symbol array
const SYMBOLS = [
    0x2588, % block
    0x25CF, % circle
    0x260E, % telefon
    0x261E, % hand white
    0x261B, % hand black
    0x263B, % smilie
    0x266B, % note
    0x2702, % scissors
    0x2712, % pencil
    0x2706, % telefon2
    0x2707, % video
    0x2708, % plane
    0x2709, % mail
    0x2756, % diamond
    0x271F, % cross
    0x2717,
    0x274D,
    0x2730,
    0x2752,
    0x271C
];

%%%%%%%%%%
% Helper %
%%%%%%%%%%
/**
 * Returns a random float between the parameter min and the parameter max.
 * @param {Number} min The lower bound.
 * @param {Number} max The upper bound.
 */
function getRandomFloat(min, max) {
    return min + Math.random() * (max - min);
}

/**
 * Returns a random integer between 0 and the parameter.
 * @param {Number} max The upper bound.
 */
function getRandomInt(max) {
    return Math.floor(Math.random() * max);
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Initialisation and Restart %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialize the default game state.
 */
function initialise() {
    % Initialize the GUI
    initialiseButtons();

    % Player rendering
    drawPlayer();

    % Draw continuously
    gameInterval = app.setInterval("gameLoop()", ANIMATION_SPEED);
    printInfoText("Initialised game!");
}

/**
 * Initialize all buttons from the GUI.
 * For example add callbacks and set the correct colors.
 */
function initialiseButtons() {
    % Disables the rectangle around a button after the click
    app.focusRect = false;

    % Allow for input
    this.getField("input1").setFocus();

    % Adjust text size and font
    var line;
    for (var m = 0; m < CANVAS_CHAR_H; m++) {
        line = this.getField("line" + m);
        line.textSize = SCREEN_TEXT_SIZE / CANVAS_CHAR_W;
        line.textFont = font.Cour;
    }

    % Init player
    var cell = this.getField("player");
    cell.value = String.fromCharCode(0x261B);
    cell.textSize = TEXT_SIZE;
    cell.hidden = false;

    % Init obstacles
    for (var i = 0; i < OBSTACLE_COUNT; i++) {
        obstacles.push([-1, -1, "#"]);
        cell = this.getField("obstacle" + i);
        cell.textSize = TEXT_SIZE;
    }

    % Assign each button the corresponding function and disable the highlights
    this.getField("restart").setAction("MouseUp", "restart();");

    % Tooltip setup
    this.getField("tooltipbtn").setAction("MouseDown", "tooltip(true);");
    this.getField("tooltipbtn").setAction("MouseUp", "tooltip(false);");
}

/**
 * Restart the game and clear everything
 */
function restart() {
    % If in animation do not restart
    if (charCounter < CANVAS_CHAR_W) {
        return;
    }
    % In case the user restarted without gameover
    if (!gameover) {
        app.clearInterval(gameInterval);
    }
    gameover = false;
    charCounter = 0;

    % Reset for input
    focus = true;
    this.getField("input1").setFocus();

    % Reset canvas
    for (var m = 0; m < CANVAS_CHAR_H; m++) {
        setLine("line" + m,  "");
    }

    % Reset player
    playerMomentum = [0.0, 0.0];
    playerPos = [CANVAS_CENTER_W * 0.5 + PLAYER_WIDTH, CANVAS_CENTER_H];
    drawPlayer();

    % Reset obstacles
    for (var i = 0; i < OBSTACLE_COUNT; i++) {
        obstacles[i] = [-1, -1, "#"];
        % Reset highlight
        markObstacle(i, false);
    }
    % Draw the obstacles
    drawObstacles();

    % Draw continuously
    gameInterval = app.setInterval("gameLoop()", ANIMATION_SPEED);
    printInfoText("Restarted game!");
}

/**
 * Enable or disable the tooltip.
 *
 * @param {Boolean} on Enable or disable tooltip.
 */
function tooltip(on) {
    if (on) {
        % Move the tooltip field to the center of the screen
        % and adjust the size so the text can be displayed
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = false;
        field.value = GAME_DESC;

        field.multiline = true;
        field.textSize = 16;
        % height 842, width 596
        % upper-left x, upper-left y, lower-right x and lower-right y
        field.rect = [128, 601, 468, 401];

        this.getField("tooltiptxt").setFocus();

        field.delay = false;
    } else {
        % Remove the field such that it is not visible
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = true;
        field.delay = false;
    }
}

%%%%%%%%%%%%%
% Gamelogic %
%%%%%%%%%%%%%
/**
 * The game loop. This is called repeatedly until the game is over.
 * It handles all game events like input, movement, spawning and
 * canvas adjustments. Each iteration is similar to one frame.
 */
function gameLoop() {
    % Cancel the interval
    if (gameover) {
        app.clearInterval(gameInterval);
        printInfoText("Game over");
        return;
    }

    % Player movement, starts after the canvas is filled
    if (charCounter >= CANVAS_CHAR_W) {
        processInput();
        applyGravityToPlayer();
    }

    % Check for collision and gameover
    var res = testCollisionObstacle();
    if (res != -1) {
        gameover = true;
        % Mark collided obstacle
        markObstacle(res, true);
        return;
    }
    % Check for collision with top or bot line
    if (testCollisionLine()) {
        gameover = true;
        return;
    }

    % Draw the canvas
    drawCanvas();

    % Starts after the canvas is filled
    if (charCounter >= CANVAS_CHAR_W) {
        % Refresh obstacles
        refreshObstacles();
        % Draw the obstacles
        drawObstacles();
    }

    % Player rendering
    drawPlayer();

    % Show current points or indicate that the game has not started yet.
    if (charCounter < CANVAS_CHAR_W) {
        printInfoText("Wait for the game to finish generating.");
    } else {
        printInfoText("You have currently " + (charCounter - CANVAS_CHAR_W) + " points.");
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Obstacles and collision %
%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Iterates all obstacles and either moves them or spawns it anew if
 * it has not spawned yet or reached the left border of the canvas.
 * Each obstacle gets a random y-value and a random symbol when spawning.
 */
function refreshObstacles() {
    % Calculate units per line
    const PER_LINE = CANVAS_HEIGHT / CANVAS_CHAR_H;

    var spawn = getRandomFloat(0.0, 1.0) > 0.9;
    for (var i = 0; i < OBSTACLE_COUNT; i++) {
        % Spawn obstacle if allowed
        if (obstacles[i][X] < CANVAS_LTRB[LEFT] && spawn) {
            var x = CANVAS_LTRB[RIGHT] + OBSTACLE_WIDTH;
            % Calculate the Y-area in which spawning is allowed
            % Get current lines
            var curTop = getLine(charCounter, START_TOP_LINE);
            var curBot = getLine(charCounter, START_BOT_LINE);
            % Get bounds in units while keeping the lines in mind
            var uBound = CANVAS_LTRB[TOP] - curTop * PER_LINE - OBSTACLE_WIDTH;
            var lBound = CANVAS_LTRB[BOT] + (CANVAS_CHAR_H - curBot) * PER_LINE + OBSTACLE_WIDTH;
            var y = getRandomFloat(lBound, uBound);

            var symb = String.fromCharCode(SYMBOLS[getRandomInt(SYMBOLS.length)]);
            obstacles[i] = [x, y, symb];
            % Only allow spawning once per frame
            spawn = false;
        } else {
            % Move obstacle such that the speed matches the movement of the boundary
            const OBSTACLE_MOVE_SPEED = 6;
            obstacles[i][X] -= OBSTACLE_MOVE_SPEED;
        }
    }
}

/**
 * Checks all obstacles if they collide with the player, if so returns the
 * object that was the collider.
 * @return {Number} The index of the collider obstacle.
 */
function testCollisionObstacle() {
    const pLeft = playerPos[X] - PLAYER_WIDTH;
    const pTop = playerPos[Y] + PLAYER_WIDTH;
    const pRight = playerPos[X] + PLAYER_WIDTH;
    const pBot = playerPos[Y] - PLAYER_WIDTH;

    % For all obstacles run a intersection test
    for (var i = 0; i < OBSTACLE_COUNT; i++) {
        var bLeft = obstacles[i][X] - PLAYER_WIDTH;
        var bTop = obstacles[i][Y] + PLAYER_WIDTH;
        var bRight = obstacles[i][X] + PLAYER_WIDTH;
        var bBot = obstacles[i][Y] - PLAYER_WIDTH;

        if (pLeft < bRight && pRight > bLeft &&
            pTop > bBot && pBot < bTop) {
            return i;
        }
    }

    return -1;
}

%
/**
 * Checks the current player hit box against the top and bottom line.
 * If a collision was detected true is returned.
 * @return {Boolean} True if collision was detected, else false.
 */
function testCollisionLine() {
    const pLeft = playerPos[X] - PLAYER_WIDTH;
    const pTop = playerPos[Y] + PLAYER_WIDTH;
    const pRight = playerPos[X] + PLAYER_WIDTH;
    const pBot = playerPos[Y] - PLAYER_WIDTH;
    const pMid = (pRight - pLeft) * 0.5 + pLeft;

    % Approximate the current char position at the center of the player
    % and get the top and bot line at that position.
    % Sample-positions does not move horizontally
    const sample = Math.round(pMid / PER_CHAR);
    var curTop = getLine(charCounter - CANVAS_CHAR_W + sample, START_TOP_LINE);
    var curBot = getLine(charCounter - CANVAS_CHAR_W + sample, START_BOT_LINE);

    % Compare the player height with the top and bot line height
    if (CANVAS_LTRB[TOP] - curTop * PER_LINE < pTop) {
        return true;
    } else if (CANVAS_LTRB[TOP] - curBot * PER_LINE > pBot) {
        return true;
    }

    return false;
}

%%%%%%%%%%%%%%%%%%%%%%
% Input and movement %
%%%%%%%%%%%%%%%%%%%%%%
/**
 * Process input made by keys of the keyboard.
 * For this multiple input fields are needed for which the focus is shifted.
 * The input is then parsed into actual movement.
 * In this case only w and space inputs are processed.
 */
function processInput() {
    var iField1 = this.getField("input1");
    var iField2 = this.getField("input2");

    % Get the input from the currently focused input element
    var movementString;
    if (focus) {
        iField1.setFocus();
        movementString = iField2.value;
        iField2.value = "";
    } else {
        iField2.setFocus();
        movementString = iField1.value
        iField1.value = "";
    }
    focus = !focus;

    % Process the input string
    if (movementString.length > 0) {
        % If the correct input occurred give the player a small force push in top direction.
        var char = movementString.charAt(0);
        if (char == "w" || char == " ") {
            force[Y] = 2.0;
        }
    } else {
        force[Y] = 0.0;
    }
}

/**
 * Alters the position and momentum of the player by using gravity and force.
 * Very similar the implementation found here:
 * https://gamedev.stackexchange.com/questions/10277/equation-for-bouncing-graph
 */
function applyGravityToPlayer() {
    const g = GRAVITY;
    const f = force;
    const m = PLAYER_MASS;
    var mom = playerMomentum;

    % Momentum += gravity + force
    mom = [mom[X] + g[X] + f[X], mom[Y] + g[Y] + f[Y]];
    % Velocity = momentum / mass
    var v = [mom[X] / m, mom[Y] / m];
    % Position += velocity
    var newPos = [playerPos[X] + v[X], playerPos[Y] + v[Y]];

    playerMomentum = mom;
    playerPos = newPos;
}

%%%%%%%%%%%%%%%%%%%%%
% Draw and coloring %
%%%%%%%%%%%%%%%%%%%%%
/**
 * Calculate the current y-position for the given x-position.
 * The y-positions are generated by a sin-function around the given baseline.
 * @param {Number} xPos The x-position for which the y-position shall be returned.
 * @param {Number} baseline The y-height around which the sin-function should run.
 * @return {Number} The calculated y-position.
 */
function getLine(xPos, baseline) {
    const period = 1;
    var rad = (xPos / CANVAS_CHAR_W) * Math.PI * 2.0 * period;
    return Math.round(Math.sin(rad) * LINE_OFFSET + baseline);
}

/**
 * Shows next frame for the canvas, by adding the next symbol at the right and
 * shifting all lines one to the left.
 * For the top and bot line a * is printed all other lines get a space.
 */
function drawCanvas() {
    % Get the top and bot line
    var tL = getLine(charCounter, START_TOP_LINE);
    var bL = getLine(charCounter, START_BOT_LINE);

    % Shift all lines
    for (var m = 0; m < CANVAS_CHAR_H; m++) {
        var symb = " ";
        if (m == tL || m == bL) {
            symb = "*";
        }

        addToLine("line" + m,  symb);

        % Shift only after the canvas was filled once
        if (charCounter >= CANVAS_CHAR_W) {
            shiftLineLeft("line" + m);
        }
    }
    charCounter++;
}

/**
 * Draws the box of the player by using its position and
 * adding the PLAYER_WIDTH to it.
 */
function drawPlayer() {
    var player = this.getField("player");
    player.delay = true;

    % upper-left x, upper-left y, lower-right x and lower-right y
    player.rect = [
        playerPos[X] - PLAYER_WIDTH,
        playerPos[Y] + PLAYER_WIDTH,
        playerPos[X] + PLAYER_WIDTH,
        playerPos[Y] - PLAYER_WIDTH
    ];

    player.delay = false;
}

/**
 * Draws all obstacles by iterating through them and adjusting their rectangle.
 * The rectangle is capped at the left border and gradually appears at the right
 * border of the canvas. Sets also the value of the cell to the obstacle symbol.
 */
function drawObstacles() {
    for (var i = 0; i < OBSTACLE_COUNT; i++) {
        var obstacle = this.getField("obstacle" + i);
        obstacle.delay = true;
        obstacle.value = obstacles[i][SYMB];

        % upper-left x, upper-left y, lower-right x and lower-right y
        % Min and max are used to cap the rectangle at the borders.
        % This leads to a gradually (dis-)appearance at the borders.
        obstacle.rect = [
            Math.min(
                Math.max(obstacles[i][X] - PLAYER_WIDTH, CANVAS_LTRB[LEFT]),
                CANVAS_LTRB[RIGHT]
            ),
            obstacles[i][Y] + PLAYER_WIDTH,
            Math.min(
                Math.max(obstacles[i][X] + PLAYER_WIDTH, CANVAS_LTRB[LEFT]),
                CANVAS_LTRB[RIGHT]
            ),
            obstacles[i][Y] - PLAYER_WIDTH
        ];

        obstacle.delay = false;
    }
}

/**
 * Enables or disables the blue highlight mode for the given obstacle id.
 * @param {Number} obs The obstacle id.
 * @param {Boolen} enable True for enabling, else false.
 */
function markObstacle(obs, enable) {
    var obstacle = this.getField("obstacle" + obs);
    obstacle.delay = true;
    if (enable) {
        obstacle.borderColor = color.blue;
    } else {
        obstacle.borderColor = color.transparent;
    }
    obstacle.delay = false;
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modify cell/line values %
%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Shift the value of the given line.
 *
 * @param {Number} id The id of the line.
 */
function shiftLineLeft(id) {
    var line = this.getField(id);
    line.delay = true;
    line.value = line.value.substring(1);
    line.delay = false;
}

/**
 * Set string of the given line.
 *
 * @param {Number} id The id of the line.
 * @param {String} value The value to set.
 */
function setLine(id, value) {
    var line = this.getField(id);
    line.delay = true;
    line.value = value;
    line.delay = false;
}

/**
 * Add string to the given line.
 *
 * @param {Number} id The id of the line.
 * @param {String} value The value to add.
 */
function addToLine(id, value) {
    var line = this.getField(id);
    line.delay = true;
    line.value += value;
    line.delay = false;
}

/**
 * Print information about the winner and the gamestate.
 */
function printInfoText(text) {
    var field = this.getField("info");
    field.delay = true;
    field.value = text;
    field.delay = false;
}

\end{insDLJS}

\OpenAction{/S /JavaScript /JS (initialise();)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dokument
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

    \begin{Form}

        % Header
        \begin{multicols}{2}
            % Title
            \section*{Side-Scroller}
        \columnbreak
            % Tooltip object
            \begin{flushright}%
                \PushButton[name=tooltipbtn, bordercolor=, backgroundcolor=, borderwidth=0]{%
                    \begin{tcolorbox}[width=20pt, height=20pt, left=3pt, top=0pt]
                        \centering?\strut{}
                    \end{tcolorbox}%
                }
            \end{flushright}%
        \end{multicols}

        % Calculate the max width and height of a cell
        \def\lineHeight{\dimexpr (500 pt)/\canvasCharHeight \relax}
        \def\lineWidth{\dimexpr (500 pt) \relax}

        \begin{center}
            \xintFor* #1 in {\xintSeq{0}{\canvasCharHeight-1}} \do {%
                \TextField[name=line#1, width=\lineWidth, height=\lineHeight,%
                    bordercolor=, readonly%
                ]{}%
                \\[0pt]%
            }%
        \end{center}

        %%%%%%%%%%%%%%%%
        % GUI elements %
        %%%%%%%%%%%%%%%%
        \begin{center}
            % Game related buttons
            \begin{tabularx}{\textwidth}{@{} *{2}{X} @{}}%
                \PushButton[name=restart, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Restart game\strut
                    \end{tcolorbox}
                } &
                \begin{tcolorbox}
                    \TextField[name=info, width=\linewidth,
                        bordercolor=, backgroundcolor=, readonly]{}
                \end{tcolorbox}
            \end{tabularx}
        \end{center}

        \TextField[name=input1, width=2in, bordercolor={0.650 .790 .94}]{}
        \TextField[name=input2, width=2in, bordercolor={0.650 .790 .94}]{}

        \TextField[name=player, width=1cm, height=1cm,
            bordercolor=, backgroundcolor=, align=1, readonly, hidden
        ]{}

        \xintFor* #1 in {\xintSeq{0}{\obstacleCount-1}} \do {%
            \TextField[name=obstacle#1, width=1cm, height=1cm,%
                bordercolor=, backgroundcolor=, align=1, readonly%
            ]{}%
        }%

        \TextField[name=tooltiptxt, bordercolor=, backgroundcolor=gray, readonly, hidden]{}

    \end{Form}
\end{document}
