\documentclass[12pt, a4paper, footexclude, headexclude]{scrartcl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=0.5in]{geometry}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}

\usepackage{xinttools}
\usepackage[nomessages]{fp}
\usepackage{tabularx}
\usepackage{tcolorbox}

\setlength{\parindent}{0pt}

% Einbindung von Javascript ins PDF
\usepackage[pdftex]{insdljs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parameter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Obacht: It is discuraged to use a field with size bigger than 15x15 since the pdf might get
% to slow to play
\def\fieldWidth{9}
\def\fieldHeight{9}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Javascript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Inhalt der Umgebung wird in JSDateiname.djs gespeichert und steht im PDF zur Verfügung
\begin{insDLJS}[]{JSDateiname}{Solo Noble}

const GAME_DESC = "The goal of this game is to generate matches. A match is defined as at least\
three cells that contain the same symbol. To build a match the player is allowed to swap the\
symbol of two adjacent cells. If the swap would indeed led to a match, the cells are swaped\
and the match is removed. The free cells are refilled by the symbols of the cells above it.\
The topmost cells are filled randomly. Chain reactions are desired.";

% Outside variables
const FIELD_WIDTH = AFMakeNumber(\fieldWidth);
const FIELD_HEIGHT = AFMakeNumber(\fieldHeight);
const SCREEN_TEXT_WIDTH = 200;

% Constants
const ANIMATION_SPEED = 500;
% For empty cells
const NONE = -1;
const EMPTY = 0;
const FULL = 1;

% Globals
% Animation interval variable
var run;
% The game field
var complField = new Array();
% Saves the last clicked cell
var currentCell = null;

%%%%%% Field arrays %%%%
const FIELD_1 = [
    [NONE, NONE,  NONE,  NONE,  NONE,  NONE,  NONE,  NONE, NONE],
    [NONE, NONE,  NONE,  FULL,  FULL,  FULL,  NONE,  NONE, NONE],
    [NONE, NONE,  NONE,  FULL,  FULL,  FULL,  NONE,  NONE, NONE],
    [NONE, FULL,  FULL,  FULL,  FULL,  FULL,  FULL,  FULL, NONE],
    [NONE, FULL,  FULL,  FULL, EMPTY,  FULL,  FULL,  FULL, NONE],
    [NONE, FULL,  FULL,  FULL,  FULL,  FULL,  FULL,  FULL, NONE],
    [NONE, NONE,  NONE,  FULL,  FULL,  FULL,  NONE,  NONE, NONE],
    [NONE, NONE,  NONE,  FULL,  FULL,  FULL,  NONE,  NONE, NONE],
    [NONE, NONE,  NONE,  NONE,  NONE,  NONE,  NONE,  NONE, NONE]
]

% Symbol array
const MARBLE_SYMBOL = String.fromCharCode(0x260E);

const MARBLE_COUNTS = [
    32, 0, 0
]

% Color data
var colors = new Array();

const HIGHLIGHT_COLOR = [ "RGB", 0.984, 0.800, 0.176 ];

%%%%%%%%%%
% Helper %
%%%%%%%%%%
/**
 * Returns a random number between 0 and the param.
 * @param {Number} max The upperbound
 */
function getRandomInt(max) {
    return Math.floor(Math.random() * max);
}

/**
 * Converts an HSL color value to RGB. Conversion formula
 * adapted from http://en.wikipedia.org/wiki/HSL_color_space.
 * Assumes h, s, and l are contained in the set [0, 1] and
 * returns r, g, and b in the set [0, 1].
 * https://stackoverflow.com/questions/2353211/hsl-to-rgb-color-conversion
 *
 * @param {number} h The hue
 * @param {number} s The saturation
 * @param {number} l The lightness
 * @return {Array} The RGB representation
 */
function hslToRgb(h, s, l) {
    var r, g, b;

    % achromatic
    if (s == 0) {
        r = g = b = l;
    } else {
        var hue2rgb = function hue2rgb(p, q, t) {
            if (t < 0) t += 1.0;
            if (t > 1) t -= 1.0;
            if (t < 1.0/6.0) return p + (q - p) * 6.0 * t;
            if (t < 1.0/2.0) return q;
            if (t < 2.0/3.0) return p + (q - p) * (2.0/3.0 - t) * 6.0;
            return p;
        }

        var q = l < 0.5 ? l * (1.0 + s) : l + s - l * s;
        var p = 2.0 * l - q;
        r = hue2rgb(p, q, h + 1.0/3.0);
        g = hue2rgb(p, q, h);
        b = hue2rgb(p, q, h - 1.0/3.0);
    }

    return [ "RGB", r, g, b ];
}

/**
 * Generates the specified amount of colors and pushes
 * them to the colors array.
 * For generating the colors are selected using hsl
 * and afterwards transformed to rgb.
 *
 * @param {number} amount The amount of colors to generate
 * @param {number} saturation The saturation
 * @param {number} lightness The lightness
 */
function generateColors(saturation, lightness, amount) {
    var huedelta = 1.0 / amount;

    for (var j = 0; j < amount; j++) {
        var hue = j * huedelta;
        colors.push(hslToRgb(hue, saturation, lightness));
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Initialisation and Restart %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialise the default game state.
 */
function initialise() {
    % Init the GUI
    initialiseButtons();

    % Create the field choosing a random symbol for each field
    var idx = 0;
    for (var row = 0; row < FIELD_HEIGHT; row++) {
        var tmp = new Array();
        for (var column = 0; column < FIELD_WIDTH; column++) {
            var cIdx = -1;
            var cell = FIELD_1[row][column];
            if (cell == FULL) {
                cIdx = idx;
                idx++;
            }
            tmp.push([cell, cIdx]);
        }
        complField.push(tmp);
    }

    hideCells();

    generateColors(1.0, 0.5, MARBLE_COUNTS[0]);

    drawAll();
}

/**
 * Initialise all buttons from the GUI.
 * For example add callbacks and set the correct colors.
 */
function initialiseButtons() {
    var field;
    % Disables the rectangle around a button after the click
    app.focusRect = false;

    % Assign each button the coresponding function and set the highlights
    this.getField("restart").setAction("MouseUp", "restart();");
    this.getField("restart").highlight="outline";

    % Each field needs to be connected to an input function
    var funcName = "fieldClicked";
    for (var x = 0; x < FIELD_WIDTH; x++) {
        for (var y = 0; y < FIELD_HEIGHT; y++) {
            var callbackName = funcName + "(" + x.toString() + "," + y.toString() + ");";
            field = this.getField("pos" + x + "-" + y);
            field.setAction("MouseDown", callbackName);
            field.textSize = SCREEN_TEXT_WIDTH / FIELD_WIDTH;
            field.alignment = "center";
        }
    }

    % Info field setup
    this.getField("info").textFont = font.Times;

    % Tooltip setup
    field = this.getField("tooltipbtn");
    field.setAction("MouseDown", "tooltip(true);");
    field.setAction("MouseUp", "tooltip(false);");
    field.highlight="none";

    printInfoText("Init");
}

/**
 * Restart the game and clear everything
 */
function restart() {
    printInfoText("Restart");

    currentCell = null;

    % Create the field choosing a random symbol for each field
    var idx = 0;
    for (var row = 0; row < FIELD_HEIGHT; row++) {
        for (var column = 0; column < FIELD_WIDTH; column++) {
            var cell = FIELD_1[row][column];
            complField[row][column][0] = cell;
            if (cell == FULL) {
                complField[row][column][1] = idx;
                idx++;
            }
        }
    }

    % Disable left over highlights
    for (var row = 0; row < FIELD_HEIGHT; row++) {
        for (var column = 0; column < FIELD_WIDTH; column++) {
            highlight(column, row, false);
        }
    }

    hideCells();

    colors = [];
    generateColors(1.0, 0.5, MARBLE_COUNTS[0]);

    drawAll();
}

/**
 * Enable or disable the tooltip
 *
 * @param {Boolean} on Enable or disable tooltip
 */
function tooltip(on) {
    if (on) {
        % Move the tooltip field to the center of the screen
        % and adjust the size so the text can be displayed
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.value = GAME_DESC;

        field.multiline = true;
        field.textSize = 16;
        field.fillColor = color.gray;
        % hight 842, width 596
        % upper-left x, upper-left y, lower-right x and lower-right y
        field.rect = [128, 601, 468, 401];

        field.delay = false;
    } else {
        % Remove the field such that it is not visible
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.value = "";

        field.multiline = false;
        field.fillColor = color.gray;
        field.rect = [0, 0, 0, 0];

        field.delay = false;
    }
}

%%%%%%%%%%%%%
% Gamelogic %
%%%%%%%%%%%%%
/**
 * Save and highlight the last field the user clicked on.
 * Selection is only removed after clicking on the same field.
 *
 * @param {Number} x The x position.
 * @param {Number} y The y position.
 */
function fieldClicked(x, y, ignore=false) {
    if (currentCell === null) {
        if (complField[y][x][0] == FULL) {
            currentCell = [x, y];
            highlight(x, y, true);
        } else {
            printInfoText("Cell empty and not selectable.");
        }
    } else if (currentCell[0] == x && currentCell[1] == y) {
        currentCell = null;
        highlight(x, y, false);
    } else {
        var diffX = currentCell[0] - x;
        var diffY = currentCell[1] - y;
        var absX = Math.abs(diffX);
        var absY = Math.abs(diffY);

        if (absX == 2 && absY == 0 || absX == 0 && absY == 2) {
            if (complField[y][x][0] == EMPTY) {
                var x2 = x + diffX / 2;
                var y2 = y + diffY / 2;

                if (complField[y2][x2][0] == FULL) {
                    highlight(currentCell[0], currentCell[1], false);
                    jump(x, y);
                    currentCell = null;
                } else {
                    printInfoText("No cell to jump over.");
                }
            } else {
                printInfoText("Cell occupied, select other cell.");
            }
        } else {
            printInfoText("Not in range, select other cell.");
        }
    }
}

/**
 *
 * @param {Number} x The x position.
 * @param {Number} y The y position.
 */
function jump(x1, y1) {
    var x2 = currentCell[0];
    var y2 = currentCell[1];

    var diffX = x2 - x1;
    var diffY = y2 - y1;
    var x3 = x1 + diffX / 2;
    var y3 = y1 + diffY / 2;

    complField[y3][x3][0] = EMPTY;
    complField[y2][x2][0] = EMPTY;
    complField[y1][x1][0] = FULL;
    complField[y1][x1][1] = complField[y2][x2][1];
    complField[y3][x3][1] = -1;
    complField[y2][x2][1] = -1;
    draw(x1, y1);
    draw(x2, y2);
    draw(x3, y3);
    printInfoText("Jump successfull.");
}

%%%%%%%%%%%%%%%%%%%%%
% Draw and coloring %
%%%%%%%%%%%%%%%%%%%%%
/**
 *
 */
function hideCells() {
    var field;
    for (var x = 0; x < FIELD_WIDTH; x++) {
        for (var y = 0; y < FIELD_HEIGHT; y++) {
            field = this.getField("pos" + x + "-" + y);
            if (complField[y][x][0] == NONE) {
                field.hidden = true;
            } else {
                field.hidden = false;
            }
        }
    }
}

/**
 * Draw all fields.
 */
function drawAll() {
    for (var x = 0; x < FIELD_WIDTH; x++) {
        for (var y = 0; y < FIELD_HEIGHT; y++) {
            draw(x, y);
        }
    }
}

/**
 * Since only one field is updated with each input,
 * only this field needs to be redrawn.
 *
 * @param {Number} x The x position.
 * @param {Number} y The y position.
 */
function draw(x, y) {
    var field = this.getField("pos" + x + "-" + y);
    field.delay = true;

    var val = complField[y][x][0];
    if (val == FULL) {
        field.value = MARBLE_SYMBOL;
        field.textColor = colors[complField[y][x][1]];
    } else {
        field.value = "";
        field.textColor = color.black;
    }
    field.delay = false;
}

/**
 * Enables or disables the highlight for
 * all cells in the field.
 *
 * @param {Boolean} enable Enables or disables highlight.
 */
function highlightAll(enable) {
    for (var row = 0; row < FIELD_HEIGHT; row++) {
        for (var column = 0; column < FIELD_WIDTH; column++) {
            highlight(column, row, enable);
        }
    }
}

/**
 * Enables or disables the highlight of the given cell.
 *
 * @param {Number} x The x position.
 * @param {Number} y The y position.
 * @param {Boolean} enable If true enables the highlight
 * @param {Boolean} bomb If true enables the bombhighlight
 */
function highlight(x, y, enable) {
    var field = this.getField("pos" + x + "-" + y);
    field.delay = true;
    % Highlight the current taken move
    if (enable) {
        field.borderColor = HIGHLIGHT_COLOR;
    } else {
        field.borderColor = color.white;
    }
    field.delay = false;
}

/**
 * Print the current points of the player.
 */
function updatePoints() {
    var field = this.getField("pointstxt");
    field.delay = true;
    field.value = points;
    field.delay = false;
}

/**
 * Print information about the gamestate.
 */
function printInfoText(text) {
    var field = this.getField("info");
    field.delay = true;
    field.value = text;
    field.delay = false;
}

\end{insDLJS}

\OpenAction{/S /JavaScript /JS (initialise();)}
\newdimen\longline
\longline=\textwidth\advance\longline-6em
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dokument
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

    \begin{Form}

        % Header
        \begin{multicols}{2}
            % Title
            \section*{Solo Noble}
        \columnbreak
            % Tooltip object
            \begin{flushright}%
                \PushButton[name=tooltipbtn, bordercolor=white]{%
                    \begin{tcolorbox}[width=20pt, height=20pt, left=3pt, top=0pt]
                        \centering?\strut{}
                    \end{tcolorbox}%
                }
            \end{flushright}%
        \end{multicols}

        % Calculate the max width and height of a block
        \FPeval{\resultW}{(\fieldWidth * 4 + 3)}
        \def\blocksizeW{\dimexpr (\linewidth-\resultW pt)/\fieldWidth \relax}

        \FPeval{\resultH}{(\fieldHeight * 4 + 3)}
        \def\blocksizeH{\dimexpr (500 pt -\resultH pt)/\fieldHeight \relax}

        % Define the blocksize via the smaller amount
        \ifnum\blocksizeW<\blocksizeH
            \def\blocksize{\blocksizeW}
        \else
            \def\blocksize{\blocksizeH}
        \fi

        % The gamefield
        \begin{tcolorbox}
            \begin{flushright}
                \xintFor* #2 in {\xintSeq{0}{\fieldHeight-1}} \do {%
                    \xintFor* #1 in {\xintSeq{0}{\fieldWidth-1}} \do {%
                        \TextField[%
                            width=\blocksize, height=\blocksize,%
                            bordercolor=white, name=pos#1-#2, readonly]{}%
                    }\vspace{3pt}
                    \newline%
                }%
            \end{flushright}%
        \end{tcolorbox}

        %%%%%%%%%%%%%%%%
        % GUI elements %
        %%%%%%%%%%%%%%%%
        \begin{multicols}{2}
            \PushButton[name=restart, bordercolor=, backgroundcolor=, borderwidth=0]{
                \begin{tcolorbox}
                    \centering
                    Restart game\strut
                \end{tcolorbox}
            }

            \columnbreak

            \begin{tcolorbox}
                \TextField[name=info, width=2\linewidth, bordercolor=, backgroundcolor=]{\strut}
            \end{tcolorbox}
        \end{multicols}

        \ChoiceMenu[name=cmLayout, bordercolor=gray, width=2cm, combo]{Layout: }{5, 6, 7, 8}

        \TextField[bordercolor=white, name=tooltiptxt, readonly]{}
    \end{Form}
\end{document}
