\documentclass[12pt, a4paper]{scrartcl}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=0.5in]{geometry}

\usepackage[pdftex]{hyperref}
\usepackage{multicol}

\usepackage{xinttools}
\usepackage[nomessages]{fp}
\usepackage{tabularx}
\usepackage{tcolorbox}

\setlength{\parindent}{0pt}

\usepackage[pdftex]{insdljs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parameter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\boardWidth{9}
\def\boardHeight{9}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% JavaScript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{insDLJS}[]{JSDateiname}{sudoku}

const GAME_DESC = "Sudoku is a logic-based number-placement puzzle.\
The objective is to fill all empty cells with a digit from 1 to 9,\
while the placements needs to follow these rules:\
1. Each row can only contain each digit once\
2. Each column can only contain each digit once\
3. Each 3x3 area can only contain each digit once.";

% Outside variables
const BOARD_WIDTH = AFMakeNumber(\boardWidth);
const BOARD_HEIGHT = AFMakeNumber(\boardHeight);
const SCREEN_TEXT_SIZE = 300;

% Constants
const M = 0;
const N = 1;

const NUMBERS = 9;
const BOX_SIZE = 3;
const EMPTY = 0;

% Globals
% Board for current visualization and input
var complBoard = new Array();
% The complete board with applied solution
var solution = new Array();
% The board containing only the initial values
var original = new Array();

% Switch if the user wants to input a Sudoku
var customMode = false;

% Color data
const COLORS = new Array(
    [ "RGB", 1.0, 1.0, 1.0 ], % white
    [ "RGB", 0.8, 0.8, 0.8 ], % gray
    [ "RGB", 0.203, 0.603, 0.054 ], % green
    [ "RGB", 0.660, 0.178, 0.233 ], % red
    [ "RGB", 0.078, 0.305, 0.560 ]
);

%%%%%%%%%%
% Helper %
%%%%%%%%%%
/**
 * Returns a random number between 0 and the parameter.
 * @param {Number} max The upper bound
 */
function getRandomInt(max) {
    return Math.floor(Math.random() * max);
}

/**
 * Shuffles array in place.
 * https://stackoverflow.com/questions/6274339/how-can-i-shuffle-an-array
 *
 * @param {Array} a items An array containing the items.
 */
function shuffle(a) {
    var j, x, i;
    for (i = a.length - 1; i > 0; i--) {
        j = Math.floor(Math.random() * (i + 1));
        x = a[i];
        a[i] = a[j];
        a[j] = x;
    }
    return a;
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Initialization and Restart %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Initialize the default game state by clearing everything and
 * generating a Sudoku.
 */
function initialize() {
    % Initialize all arrays with a zero array
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        var row1 = new Array();
        var row2 = new Array();
        var row3 = new Array();
        for (var n = 0; n < BOARD_WIDTH; n++) {
            row1.push(EMPTY);
            row2.push(EMPTY);
            row3.push(EMPTY);
        }
        complBoard.push(row1);
        solution.push(row2);
        original.push(row3);
    }

    % Initialize the GUI
    initializeButtons();

    generateSudoku();
}

/**
 * Initialize all buttons from the GUI.
 * For example add callbacks and set the correct colors.
 */
function initializeButtons() {
    % Disables the rectangle around a button after the click
    app.focusRect = false;

    % Assign each button the corresponding function and disable the highlights
    this.getField("generate").setAction("MouseUp", "generateSudoku();");
    this.getField("hint").setAction("MouseUp", "showHint();");
    this.getField("solve").setAction("MouseUp", "showSolution();");
    this.getField("enter").setAction("MouseUp", "enterSudoku();");
    this.getField("reset").setAction("MouseUp", "resetSudoku();");

    % Selection field for the amount of predefined cells when generating
    this.getField("elemcount").borderColor = color.white;
    this.getField("elemcount").currentValueIndices = 2;
    this.getField("elemcount").commitOnSelChange = true;

    % Each cell needs to be connected to an input function
    % Define text style
    var funcName = "checkInput";
    var cell;
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            var callbackName = funcName + "(" + m.toString() + "," + n.toString() + ");";
            cell = this.getField("cell" + m + "-" + n);
            cell.setAction("OnBlur", callbackName);
            cell.textSize = SCREEN_TEXT_SIZE / Math.max(BOARD_HEIGHT, BOARD_WIDTH);
        }
    }

    % Tooltip setup
    this.getField("tooltipbtn").setAction("MouseDown", "tooltip(true);");
    this.getField("tooltipbtn").setAction("MouseUp", "tooltip(false);");
}

/**
 * Enable or disable the tooltip.
 *
 * @param {Boolean} on Enable or disable tooltip.
 */
function tooltip(on) {
    if (on) {
        % Move the tooltip field to the center of the screen
        % and adjust the size so the text can be displayed
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = false;
        field.value = GAME_DESC;

        field.multiline = true;
        field.textSize = 16;
        % height 842, width 596
        % upper-left x, upper-left y, lower-right x and lower-right y
        field.rect = [128, 601, 468, 401];

        this.getField("tooltiptxt").setFocus();

        field.delay = false;
    } else {
        % Remove the field such that it is not visible
        var field = this.getField("tooltiptxt");
        field.delay = true;
        field.hidden = true;
        field.delay = false;
    }
}

/**
 * Activate manual Sudoku input.
 */
function enterSudoku() {
    % Clear all arrays to zero
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            complBoard[m][n] = EMPTY;
            solution[m][n] = EMPTY;
            original[m][n] = EMPTY;
        }
    }

    % Save the input mode
    customMode = true;

    drawAll(false);
}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Generation and solving %
%%%%%%%%%%%%%%%%%%%%%%%%%%
/**
 * Generates a Sudoku.
 * The solution is saved inside the solution array.
 * Inside the complBoard the same values can be found
 * with some of them removed. The amount is defined by
 * the GUI element "elemcount".
 *
 * Algorithm:
 * 1. Clear array
 * 2. Fill diagonal 3x3 matrices randomly.
 * 3. Fill rest by solving the Sudoku.
 * 4. Remove K elements randomly
 * Source: https://www.geeksforgeeks.org/program-sudoku-generator/
 */
function generateSudoku() {
    customMode = false;

    % Clear array
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            complBoard[m][n] = EMPTY;
        }
    }

    % Fill all the diagonal 3x3 matrices randomly.
    var numberArray = [];
    for (var i = 1; i <= NUMBERS; i++) {
        numberArray.push(i);
    }

    % % Fill top left
    fillQuad(numberArray, 0, 0);
    % Fill middle
    fillQuad(numberArray, BOX_SIZE, BOX_SIZE);
    % Fill bot right
    fillQuad(numberArray, BOX_SIZE * 2, BOX_SIZE * 2);

    % Fill rest of the non-diagonal matrices.
    % For every cell to be filled, try all numbers until
    % a safe number is found.
    if (!solveSudoku()) {
        return;
    }

    % Remove K elements randomly
    % Get all possible position combinations
    var positions = [];
    for (var m = 0; m < NUMBERS; m++) {
        for (var n = 0; n < NUMBERS; n++) {
            positions.push([m, n]);
        }
    }
    var num_elements = this.getField("elemcount").value;
    var rnd = 0;
    for (var count = NUMBERS * NUMBERS; count > num_elements; count--) {
        % Draw and remove one random element from the positions array
        rnd = getRandomInt(positions.length);
        var elem = positions[rnd];
        complBoard[elem[M]][elem[N]] = EMPTY;
        positions.splice(rnd, 1);
    }

    % Save the current board into the original array,
    % to allow for easy reset
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            original[m][n] = complBoard[m][n];
        }
    }

    drawAll(true);

    printInfoText("Please fill the Sudoku.");
}

/**
 * Fills a 3x3 matrix with the number array that is given.
 * The number array is shuffled inside the function to
 * achieve randomness.
 *
 * @param {Array} numberArray Array of numbers to fill the quad with
 * @param {Number} offsetM Select the m position of the quad
 * @param {Number} offsetN Select the n position of the quad
 */
function fillQuad(numberArray, offsetM, offsetN) {
    shuffle(numberArray);

    var m = 0;
    var n = 0;
    % Assign each number to a cell
    for (var idx = 0; idx < numberArray.length; idx++) {
        % Wrap to next line - expects the lines to be 3 in length
        m = offsetM + Math.floor(idx / BOX_SIZE);
        n = offsetN + (idx \% BOX_SIZE);
        complBoard[m][n] = numberArray[idx];
    }
}

/**
 * Solve the Sudoku.
 *
 * Algorithm:
 * 1. Make list of all empty spaces
 * 2. For each element in list find all candidates
 * 3. Setup an array to save which combinations where tried
 * 4. Iterate all spaces
 * 4.1. Try a candidate
 * 4.2. If cell value is still valid continue
 * 4.3. Else increase iteration counter and reset space iterator
 *
 * @return { Boolean } true if successful, else false
 */
function solveSudoku() {
    % Make list of all empty spaces
    var spaces = getEmptySpaces();

    % For each element in list find all candidates
    var candidates = getCandidates(spaces);

    % This should not happen
    for (var idx = 0; idx < spaces.length; idx++) {
        if (candidates[idx].length == 0) {
            printInfoText("An error occurred in solveSudoku candidates.");
            return false;
        }
    }

    % Setup and initialize candidate indices
    var indices = [];
    for (var i = 0; i < spaces.length; i++) {
        indices.push(0);
    }

    % Apply candidates
    for (var idx = 0; idx < spaces.length; idx++) {
        complBoard[spaces[idx][M]][spaces[idx][N]] = candidates[idx][indices[idx]];

        % When the cell value is not valid increase indices and reset complBoard and idx
        if (!isCellValid(spaces[idx][M], spaces[idx][N])) {

            var tmpIdx = idx;
            % Increment the current index
            indices[tmpIdx]++;
            % This allows for checking all combinations:
            % If there is an overflow for the current index it is reset
            % and the idx - 1 is increased until a combination without
            % overflow is found
            for (; indices[tmpIdx] >= candidates[tmpIdx].length; tmpIdx--) {
                indices[tmpIdx] = 0;

                if (tmpIdx - 1 < 0) {
                    printInfoText("An error occurred in solveSudoku comb-check.");
                    return false;
                } else {
                    indices[tmpIdx - 1]++;
                }
            }

            % Reverse not valid solution
            for (var idx2 = 0; idx2 <= idx; idx2++) {
                complBoard[spaces[idx2][M]][spaces[idx2][N]] = EMPTY;
            }

            % Restart the idx counter since the solution for the spaces did not work
            idx = -1;
        }
    }

    % Save complete solution since we already generated it here
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            solution[m][n] = complBoard[m][n];
        }
    }

    return true;
}

/**
 * Returns an array of positions ([m, n]) at which
 * the complBoard contains a zero (0) and is therefore EMPTY.
 *
 * @return {Array} Array of empty spaces
 */
function getEmptySpaces() {
    var spaces = [];
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            if (complBoard[m][n] == EMPTY) {
                spaces.push([m, n]);
            }
        }
    }
    return spaces;
}

/**
 * Returns an array of candidates which number of 1-9 could be
 * put at the given spaces. These are selected by consulting the
 * typical Sudoku rules.
 *
 * @param {Array} spaces An array of empty cells
 * @return {Array} An array of candidates for each space
 */
function getCandidates(spaces) {
    % Helper array to mark all numbers that are disallowed
    var disallowed = [];
    for (var i = 0; i < 9; i++) {
        disallowed.push(true);
    }

    var candidates = [];
    var num = 0;
    % Iterate all spaces that need to be filled
    for (var idx = 0; idx < spaces.length; idx++) {
        % Check the row for all numbers that are set
        for (var n = 0; n < BOARD_WIDTH; n++) {
            num = complBoard[spaces[idx][M]][n];
            if (num > EMPTY) {
                disallowed[num - 1] = false;
            }
        }

        % Check the column for all numbers that are set
        for (var m = 0; m < BOARD_HEIGHT; m++) {
            num = complBoard[m][spaces[idx][N]];
            if (num > EMPTY) {
                disallowed[num - 1] = false;
            }
        }

        % Check the box for all numbers that are set
        var mQuad = Math.floor(spaces[idx][M] / BOX_SIZE);
        var nQuad = Math.floor(spaces[idx][N] / BOX_SIZE);
        for (var m = mQuad * BOX_SIZE; m < mQuad * BOX_SIZE + BOX_SIZE; m++) {
            for (var n = nQuad * BOX_SIZE; n < nQuad * BOX_SIZE + BOX_SIZE; n++) {
                num = complBoard[m][n];
                if (num > EMPTY) {
                    disallowed[num - 1] = false;
                }
            }
        }

        % Get candidates
        var tmpCnd = [];
        for (var i = 0; i < disallowed.length; i++) {
            if (disallowed[i]) {
                tmpCnd.push(i + 1);
            }
        }
        candidates.push(tmpCnd);

        % Reset the disallowed numbers
        for (var i = 0; i < 9; i++) {
            disallowed[i] = true;
        }
    }
    return candidates;
}

/**
 * Checks the board at the given position
 * for conflicts with the Sudoku rules
 * given the current numbers on the board.
 *
 * @param {Number} valM M-coordinate of the cell
 * @param {Number} valM N-coordinate of the cell
 * @return {Boolean} Returns true if cell value is valid else false.
 */
function isCellValid(valM, valN) {
    % Get the value
    var value = complBoard[valM][valN];

    % Check all possibly conflicting cells for the same value
    % Check the row
    for (var n = 0; n < BOARD_WIDTH; n++) {
        if (complBoard[valM][n] == value && n != valN) {
            return false;
        }
    }

    % Check the column
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        if (complBoard[m][valN] == value && m != valM) {
            return false;
        }
    }

    % Check the box
    var mQuad = Math.floor(valM / BOX_SIZE);
    var nQuad = Math.floor(valN / BOX_SIZE);
    for (var m = mQuad * BOX_SIZE; m < mQuad * BOX_SIZE + BOX_SIZE; m++) {
        for (var n = nQuad * BOX_SIZE; n < nQuad * BOX_SIZE + BOX_SIZE; n++) {
            if (complBoard[m][n] == value && (m != valM || n != valN)) {
                return false;
            }
        }
    }

    return true;
}

/**
 * Checks the given user input if it is valid.
 * Needs to be a number between 0 and 10.
 * If the value is not allowed by the Sudoku rules
 * the cell is marked red and green otherwise.
 *
 * @param {Number} m The m coordinate
 * @param {Number} n The n coordinate
 */
function checkInput(m, n) {
    % Get the value that was committed
    var cell = this.getField("cell" + m + "-" + n);

    % If the value did not change do not do anything
    if (complBoard[m][n] == cell.value) {
        return;
    }
    cell.delay = true;

    % When the value is inside the bounds
    % validate it and color the cell correspondingly.
    if (cell.value > 0 && cell.value < 10) {
        complBoard[m][n] = cell.value;
        if (isCellValid(m, n)) {
            cell.fillColor = COLORS[2];
        } else {
            cell.fillColor = COLORS[3];
        }
    }
    % Else remove the value from the cell
    else {
        cell.value = "";
        cell.fillColor = COLORS[0];
    }

    cell.delay = false;
}

%%%%%%%%%%%%%%%%%%%%%
% Draw and coloring %
%%%%%%%%%%%%%%%%%%%%%
/**
 * Resets the Sudoku to the original generated one.
 */
function resetSudoku() {
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            complBoard[m][n] = original[m][n];
            refreshCell(m, n, COLORS[1]);
        }
    }
}

/**
 * Shows one cell that was not previously revealed.
 */
function showHint() {
    % If one cell in the solution array is zero (EMPTY) the whole array should be
    % zero and therefore the solution was not yet generated
    if (solution[0][0] == EMPTY) {
        solveSudoku();
    }

    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            if (complBoard[m][n] == EMPTY) {
                complBoard[m][n] = solution[m][n];
                refreshCell(m, n, COLORS[1]);
                return;
            }
        }
    }
}

/**
 * Reveals the complete solution.
 */
function showSolution() {
    % When in custom mode it is not possible to know when
    % the user is done therefore the solution can only be
    % generated after requesting it
    if (customMode) {
        solveSudoku();
    }

    % Just copy all values from the solution array
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            if (complBoard[m][n] == EMPTY || customMode) {
                complBoard[m][n] = solution[m][n];
                refreshCell(m, n, COLORS[0]);
            }
        }
    }
}

/**
 * Refreshes value of one input cell.
 *
 * @param {Number} m The m position.
 * @param {Number} n The n position.
 * @param {Array} color The RGB color.
 *              Gray for given cells, green for correct cells,
 *              Red for wrong cells, white for empty cells.
 */
function refreshCell(m, n, color) {
    var cell = this.getField("cell" + m + "-" + n);
    cell.delay = true;
    if (complBoard[m][n] > EMPTY) {
        cell.value = complBoard[m][n];
        cell.fillColor = color;
    } else {
        cell.value = "";
        cell.fillColor = COLORS[0];
    }
    cell.delay = false;
}

/**
 * Redraw complete board, coloring can be enabled.
 *
 * @param {Boolean} color Should the cells be colored.
 */
function drawAll(color) {
    for (var m = 0; m < BOARD_HEIGHT; m++) {
        for (var n = 0; n < BOARD_WIDTH; n++) {
            cell = this.getField("cell" + m + "-" + n);
            cell.delay = true;
            if (complBoard[m][n] > EMPTY) {
                cell.value = complBoard[m][n];
                if (color) {
                    cell.fillColor = COLORS[1];
                    cell.readonly = true;
                }
            } else {
                cell.value = "";
                cell.fillColor = COLORS[0];
                cell.readonly = false;
            }
            cell.delay = false;
        }
    }
}

/**
 * Print information about the game.
 *
 * @param {String} text Info string
 */
function printInfoText(text) {
    var field = this.getField("info");
    field.delay = true;
    field.value = text;
    field.delay = false;
}

\end{insDLJS}

\OpenAction{/S /JavaScript /JS (initialize();)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

    \begin{Form}

        % Header
        \begin{multicols}{2}
            % Title
            \section*{Sudoku}
        \columnbreak
            % Tooltip object
            \begin{flushright}%
                \PushButton[name=tooltipbtn, bordercolor=, backgroundcolor=, borderwidth=0]{%
                    \begin{tcolorbox}[width=20pt, height=20pt, left=3pt, top=0pt]
                        \centering?\strut{}
                    \end{tcolorbox}%
                }
            \end{flushright}%
        \end{multicols}

        % Dynamically adjust the cell width and height to the number of cells
        % Calculate the max width and height of a cell
        \FPeval{\resultW}{\boardWidth * 4 + 3 + \boardWidth * 3}
        \def\cellWidth{\dimexpr (\linewidth-\resultW pt)/\boardWidth \relax}

        \FPeval{\resultH}{\boardHeight * 3 + 3}
        \def\cellHeight{\dimexpr (500 pt -\resultH pt)/\boardHeight \relax}

        % Playing board
        \begin{tcolorbox}
            % Define the cell size via the smaller amount
            % Must be done here so the \linewidth has the correct value
            \ifdim\cellWidth<\cellHeight
                \def\cellsize{\cellWidth}
            \else
                \def\cellsize{\cellHeight}
            \fi

            \begin{flushright}
                \xintFor* #1 in {\xintSeq{0}{\boardHeight-1}} \do {%
                    \ifnum#1=3%
                        \vspace{-12pt}%
                        \noindent\rule[13pt]{\linewidth}{1pt}
                    \fi%
                    \ifnum#1=6%
                        \vspace{-12pt}%
                        \noindent\rule[13pt]{\linewidth}{1pt}
                    \fi%
                    \vspace{1pt}%
                    \xintFor* #2 in {\xintSeq{0}{\boardWidth-1}} \do {%
                        \TextField[%
                            name=cell#1-#2, width=\cellsize, height=\cellsize,%
                            bordercolor=white, align=1%
                        ]{}%
                        \hspace{2pt}%
                        \ifnum#2=2%
                            %\vspace{1pt}%
                            \vrule width 1pt%
                        \fi%
                        \ifnum#2=5%
                            %\vspace{1pt}%
                            \vrule width 1pt%
                        \fi%
                        \hspace{2pt}%
                    }\vspace{1pt}%
                    \newline%
                }%
            \end{flushright}%
        \end{tcolorbox}
        %
        %%%%%%%%%%%%%%%%%%%%%%%
        % Commandredifinition %
        % https://www.dickimaw-books.com/latex/admin/html/eforms.shtml
        %%%%%%%%%%%%%%%%%%%%%%%
        \def\DefaultHeightofText{14pt}
        \renewcommand*{\LayoutTextField}[2]{%
            \parbox[c][\DefaultHeightofText]{\linewidth}{#1#2}%
        }

        \renewcommand*{\DefaultWidthofChoiceMenu}{2.5ex}
        \renewcommand*{\DefaultHeightofChoiceMenu}{2.04ex}

        %%%%%%%%%%%%%%%%
        % GUI elements %
        %%%%%%%%%%%%%%%
        \ChoiceMenu[name=elemcount, bordercolor=gray, width=50mm, combo]
            {Fullcell count:}{15, 30, 45, 60, 75}
        \TextField[name=tooltiptxt, bordercolor=, backgroundcolor=gray, readonly, hidden]{}
        %
        \begin{center}%
            \begin{tabularx}{\textwidth}{@{} *{2}{X} @{}}%
                \PushButton[name=generate, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Generate new Sudoku\strut
                    \end{tcolorbox}
                } &
                \PushButton[name=enter, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Enter own Sudoku\strut
                    \end{tcolorbox}
                } \\
                \PushButton[name=solve, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Show current solution\strut
                    \end{tcolorbox}
                } &
                \PushButton[name=hint, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Give me a hint\strut
                    \end{tcolorbox}
                } \\
                \PushButton[name=reset, bordercolor=, backgroundcolor=, borderwidth=0]{
                    \begin{tcolorbox}
                        \centering
                        Reset current input\strut
                    \end{tcolorbox}
                } &
                \begin{tcolorbox}
                    \TextField[name=info, width=\linewidth,
                        bordercolor=, backgroundcolor=, readonly]{}
                \end{tcolorbox}
            \end{tabularx}
        \end{center}

    \end{Form}
\end{document}
